---
title: "Sociodemographic characteristics DataSchema"
output: html_document
---
# Table of Contents
1. [Age and sex subdomain](#age-and-sex-subdomain)
2. [Employment and retirement subdomain](#employment-and-retirement-subdomain)
3. [Education and income subdomain](#education-and-income-subdomain)
4. [Ethnicity subdomain](#ethnicity-subdomain)
5. [Marital status subdomain](#marital-status-subdomain)
6. [Number of people in household subdomain](#number-of-people-in-household-subdomain)

# Age and sex subdomain

### **Variable label**: Age of participant   
**Variable name**: SDC_AGE_0     
**Variable description**: Age of participant at baseline    
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Age of participant   
**Variable name**: SDC_AGE_1     
**Variable description**: Age of participant at first follow-up     
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Age of participant   
**Variable name**: SDC_AGE_2     
**Variable description**: Age of participant at second follow-up    
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Age of participant   
**Variable name**: SDC_AGE_3     
**Variable description**: Age of participant at third follow-up    
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Age of participant   
**Variable name**: SDC_AGE_4     
**Variable description**: Age of participant at fourth follow-up    
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Age of participant   
**Variable name**: SDC_AGE_5     
**Variable description**: Age of participant at fifth follow-up    
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Age of participant   
**Variable name**: SDC_AGE_6     
**Variable description**: Age of participant at sixth follow-up    
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Gender of participant   
**Variable name**: SDC_GENDER_0     
**Variable description**: Gender of participant at baseline    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Male   
1 | Female   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
# Employment and retirement subdomain

### **Variable label**: Employment status   
**Variable name**: SDC_WRK_EMPLOYMENT_0    
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |No   
1 |Yes   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Employment status   
**Variable name**: SDC_WRK_EMPLOYMENT_1    
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |No   
1 |Yes   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Employment status   
**Variable name**: SDC_WRK_EMPLOYMENT_2    
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |No   
1 |Yes   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Retirement status   
**Variable name**: SDC_WRK_RETIREMENT_0    
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |No   
1 |Yes   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Retirement status   
**Variable name**: SDC_WRK_RETIREMENT_1    
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |No   
1 |Yes   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Retirement status   
**Variable name**: SDC_WRK_RETIREMENT_2    
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |No   
1 |Yes   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Age of participant at retirement  
**Variable name**: SDC_WRK_RETIREMENT_AGE_0    
**Variable description**: Age of participant at retirement
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Age of participant at retirement  
**Variable name**: SDC_WRK_RETIREMENT_AGE_1    
**Variable description**: Age of participant at retirement
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Age of participant at retirement  
**Variable name**: SDC_WRK_RETIREMENT_AGE_2    
**Variable description**: Age of participant at retirement
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  

# Education and income subdomain

### **Variable label**: Highest level of education completed (ISCED 1997)    
**Variable name**: SDC_HIGHEST_EDU_0     
**Variable description**: Highest level of education completed by the participant in accordance with the International Standard Classification of Education (ISCED 1997).     
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Lower secondary or less (ISCED 0-2)  
2 | Upper secondary (ISCED 3)
3 | Post-secondary non-tertiary education (ISCED 4)
4 | Tertiary education or more (ISCED 5,6)

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Highest level of education completed (ISCED 1997)    
**Variable name**: SDC_HIGHEST_EDU_1     
**Variable description**: Highest level of education completed by the participant in accordance with the International Standard Classification of Education (ISCED 1997).     
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Lower secondary or less (ISCED 0-2)  
2 | Upper secondary (ISCED 3)
3 | Post-secondary non-tertiary education (ISCED 4)
4 | Tertiary education or more (ISCED 5,6)

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Post-secondary education    
**Variable name**: SDC_HIGHSCHOOL_POST_EDU_0     
**Variable description**: Indicator of whether the participant completed highschool or post-secondary education.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Upper secondary (ISCED 3) or less
1 | Post-secondary non-tertiary education (ISCED 4) or more  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  

# Ethnicity subdomain

### **Variable label**:  
**Variable name**:  
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Marital status subdomain

### **Variable label**:  
**Variable name**:  
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```


# Number of people in household subdomain

### **Variable label**:  
**Variable name**:  
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
