---
title: "Sociodemographic characteristics DataSchema"
output: html_document
---
# Table of Contents
1. [Age and sex subdomain](#age-and-sex-subdomain)
2. [Employment and retirement subdomain](#employment-and-retirement-subdomain)
3. [Marital status subdomain](#marital-status-subdomain)
4. [Number of people in household subdomain](#number-of-people-in-household-subdomain)

# Age and sex subdomain

### **Variable label**: Age of participant   
**Variable name**: sdc_age_0      
**Variable description**: Age of the participant.      
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Age of participant   
**Variable name**: sdc_age_1       
**Variable description**: Age of the participant.      
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Age of participant   
**Variable name**: sdc_age_2     
**Variable description**: Age of the participant.      
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Age of participant   
**Variable name**: sdc_age_3     
**Variable description**: Age of the participant.     
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Age of participant   
**Variable name**: sdc_age_4       
**Variable description**: Age of the participant.      
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Age of participant   
**Variable name**: sdc_age_5     
**Variable description**: Age of the participant.      
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Age of participant   
**Variable name**: sdc_age_6     
**Variable description**: Age of the participant.      
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Gender of participant   
**Variable name**: sdc_gender_0       
**Variable description**: Gender of the participant.      
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Male   
1 | Female   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
# Employment and retirement subdomain

### **Variable label**: Employment status   
**Variable name**: sdc_wrk_employ_0       
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in paid employment   
1 | Currently in paid employment

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Employment status   
**Variable name**: sdc_wrk_employ_1    
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in paid employment   
1 | Currently in paid employment  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Employment status   
**Variable name**: sdc_wrk_employ_2    
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in paid employment   
1 | Currently in paid employment   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Employment status   
**Variable name**: sdc_wrk_employ_3    
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in paid employment   
1 | Currently in paid employment   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Employment status   
**Variable name**: sdc_wrk_employ_4    
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in paid employment   
1 | Currently in paid employment   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Employment status   
**Variable name**: sdc_wrk_employ_5    
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in paid employment   
1 | Currently in paid employment   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Employment status   
**Variable name**: sdc_wrk_employ_6    
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in paid employment   
1 | Currently in paid employment   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Retirement status   
**Variable name**: sdc_wrk_retire_0     
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | currently not in retirement   
1 | currently in retirement   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Retirement status   
**Variable name**: sdc_wrk_retire_1     
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | currently not in retirement   
1 | currently in retirement   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Retirement status   
**Variable name**: sdc_wrk_retire_2     
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | currently not in retirement   
1 | currently in retirement   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Retirement status   
**Variable name**: sdc_wrk_retire_3     
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | currently not in retirement   
1 | currently in retirement   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Retirement status   
**Variable name**: sdc_wrk_retire_4     
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | currently not in retirement   
1 | currently in retirement   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Retirement status   
**Variable name**: sdc_wrk_retire_5     
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | currently not in retirement   
1 | currently in retirement   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Retirement status   
**Variable name**: sdc_wrk_retire_6      
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | currently not in retirement   
1 | currently in retirement   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Age of participant at retirement  
**Variable name**: sdc_wrk_retire_age_0      
**Variable description**: Age of the participant at retirement.  
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Age of participant at retirement  
**Variable name**: sdc_wrk_retire_age_1    
**Variable description**: Age of the participant at retirement.  
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Age of participant at retirement  
**Variable name**: sdc_wrk_retire_age_2    
**Variable description**: Age of the participant at retirement.    
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  

# Education and income subdomain

### **Variable label**: Highest level of education completed (ISCED 2011)    
**Variable name**: sdc_highest_edu_0       
**Variable description**: Highest level of education completed by the participant in accordance with the International Standard Classification of Education (ISCED 2011).       
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Lower secondary or less (ISCED 0-2)  
2 | Upper secondary (ISCED 3)
3 | Post-secondary non-tertiary education or short-cycle tertiary education (ISCED 4,5)
4 | Bachelor,master,doctoral or equivalent (ISCED 6,7,8)

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Highest level of education completed (ISCED 2011)    
**Variable name**: sdc_highest_edu_1     
**Variable description**: Highest level of education completed by the participant in accordance with the International Standard Classification of Education (ISCED 2011).     
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Lower secondary or less (ISCED 0-2)  
2 | Upper secondary (ISCED 3)
3 | Post-secondary non-tertiary education or short-cycle tertiary education (ISCED 4,5)
4 | Bachelor,master,doctoral,or equivalent (ISCED 6,7,8)

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Highest level of education completed (ISCED 2011)    
**Variable name**: sdc_highest_edu_2     
**Variable description**: Highest level of education completed by the participant in accordance with the International Standard Classification of Education (ISCED 2011).     
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Lower secondary or less (ISCED 0-2)  
2 | Upper secondary (ISCED 3)
3 | Post-secondary non-tertiary education or short-cycle tertiary education (ISCED 4,5)
4 | Bachelor,master,doctoral,or equivalent (ISCED 6,7,8)

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Highest level of education completed (ISCED 2011)    
**Variable name**: sdc_highest_edu_3     
**Variable description**: Highest level of education completed by the participant in accordance with the International Standard Classification of Education (ISCED 2011).     
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Lower secondary or less (ISCED 0-2)  
2 | Upper secondary (ISCED 3)
3 | Post-secondary non-tertiary education or short-cycle tertiary education (ISCED 4,5)
4 | Bachelor,master,doctoral,or equivalent (ISCED 6,7,8)

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Highest level of education completed (ISCED 2011)    
**Variable name**: sdc_highest_edu_4     
**Variable description**: Highest level of education completed by the participant in accordance with the International Standard Classification of Education (ISCED 2011).     
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Lower secondary or less (ISCED 0-2)  
2 | Upper secondary (ISCED 3)
3 | Post-secondary non-tertiary education or short-cycle tertiary education (ISCED 4,5)
4 | Bachelor,master,doctoral,or equivalent (ISCED 6,7,8)

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Post-secondary education    
**Variable name**: sdc_highschool_post_edu_0       
**Variable description**: Indicator of whether the participant completed highschool or post-secondary education.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Upper secondary or less (ISCED 0-3)
1 | Post-secondary non-tertiary education or more (ISCED 4-8)  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Post-secondary education    
**Variable name**: sdc_highschool_post_edu_1     
**Variable description**: Indicator of whether the participant completed highschool or post-secondary education.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Upper secondary or less (ISCED 0-3)
1 | Post-secondary non-tertiary education or more (ISCED 4-8)    

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Post-secondary education    
**Variable name**: sdc_highschool_post_edu_2     
**Variable description**: Indicator of whether the participant completed highschool or post-secondary education.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Upper secondary or less (ISCED 0-3)
1 | Post-secondary non-tertiary education or more (ISCED 4-8)    

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Post-secondary education    
**Variable name**: sdc_highschool_post_edu_3     
**Variable description**: Indicator of whether the participant completed highschool or post-secondary education.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Upper secondary or less (ISCED 0-3)
1 | Post-secondary non-tertiary education or more (ISCED 4-8)    

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Post-secondary education    
**Variable name**: sdc_highschool_post_edu_4     
**Variable description**: Indicator of whether the participant completed highschool or post-secondary education.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Upper secondary or less (ISCED 0-3)
1 | Post-secondary non-tertiary education or more (ISCED 4-8)    

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Net annual household income    
**Variable name**: sdc_income_0       
**Variable description**: Indicator of whether the net annual household income is above or below the country-specific net mean household income.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income    

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Net annual household income    
**Variable name**: sdc_income_1       
**Variable description**: Indicator of whether the net annual household income is above or below the country-specific net mean household income.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income    

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```    
### **Variable label**: Net annual household income    
**Variable name**: sdc_income_2       
**Variable description**: Indicator of whether the net annual household income is above or below the country-specific net mean household income.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income    

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```   
### **Variable label**: Net annual household income    
**Variable name**: sdc_income_3       
**Variable description**: Indicator of whether the net annual household income is above or below the country-specific net mean household income.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income    

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```   
### **Variable label**: Net annual household income    
**Variable name**: sdc_income_4       
**Variable description**: Indicator of whether the net annual household income is above or below the country-specific net mean household income.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income    

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```   
### **Variable label**: Net annual household income    
**Variable name**: sdc_income_5       
**Variable description**: Indicator of whether the net annual household income is above or below the country-specific net mean household income.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income    

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Net annual household income    
**Variable name**: sdc_income_6       
**Variable description**: Indicator of whether the net annual household income is above or below the country-specific net mean household income.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income    

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
# Marital status subdomain

### **Variable label**: Civil status    
**Variable name**: sdc_civil_status_0      
**Variable description**: Indicator of the participant's current civil status  
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently single or unmarried   
1 | Currently married or living with partner
2 | Currently divorced or separated
3 | Currently widowed  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Civil status    
**Variable name**: sdc_civil_status_1      
**Variable description**: Indicator of the participant's current civil status  
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently single or unmarried   
1 | Currently married or living with partner
2 | Currently divorced or separated
3 | Currently widowed  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```   
### **Variable label**: Civil status    
**Variable name**: sdc_civil_status_2      
**Variable description**: Indicator of the participant's current civil status  
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently single or unmarried   
1 | Currently married or living with partner
2 | Currently divorced or separated
3 | Currently widowed  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```   
### **Variable label**: Civil status    
**Variable name**: sdc_civil_status_3        
**Variable description**: Indicator of the participant's current civil status  
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently single or unmarried   
1 | Currently married or living with partner
2 | Currently divorced or separated
3 | Currently widowed  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Civil status    
**Variable name**: sdc_civil_status_4      
**Variable description**: Indicator of the participant's current civil status  
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently single or unmarried   
1 | Currently married or living with partner
2 | Currently divorced or separated
3 | Currently widowed  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```   
### **Variable label**: Civil status    
**Variable name**: sdc_civil_status_5      
**Variable description**: Indicator of the participant's current civil status  
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently single or unmarried   
1 | Currently married or living with partner
2 | Currently divorced or separated
3 | Currently widowed  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```   
### **Variable label**: Civil status    
**Variable name**: sdc_civil_status_6      
**Variable description**: Indicator of the participant's current civil status  
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently single or unmarried   
1 | Currently married or living with partner
2 | Currently divorced or separated
3 | Currently widowed  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```    
### **Variable label**: Married or living with partner  
**Variable name**: sdc_marital_stat_living_part_0      
**Variable description**: Indicator of whether the participant is currently married or is currently living with a spouse or a partner in a common household.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not married or living with partner   
1 | Currently married or living with partner  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Married or living with partner  
**Variable name**: sdc_marital_stat_living_part_1      
**Variable description**: Indicator of whether the participant is currently married or is currently living with a spouse or a partner in a common household.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not married or living with partner   
1 | Currently married or living with partner  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```   
### **Variable label**: Married or living with partner  
**Variable name**: sdc_marital_stat_living_part_2      
**Variable description**: Indicator of whether the participant is currently married or is currently living with a spouse or a partner in a common household.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not married or living with partner   
1 | Currently married or living with partner  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Married or living with partner  
**Variable name**: sdc_marital_stat_living_part_3      
**Variable description**: Indicator of whether the participant is currently married or is currently living with a spouse or a partner in a common household.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not married or living with partner   
1 | Currently married or living with partner  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Married or living with partner  
**Variable name**: sdc_marital_stat_living_part_4      
**Variable description**: Indicator of whether the participant is currently married or is currently living with a spouse or a partner in a common household.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not married or living with partner   
1 | Currently married or living with partner  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Married or living with partner  
**Variable name**: sdc_marital_stat_living_part_5      
**Variable description**: Indicator of whether the participant is currently married or is currently living with a spouse or a partner in a common household.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not married or living with partner   
1 | Currently married or living with partner  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```    
### **Variable label**: Married or living with partner  
**Variable name**: sdc_marital_stat_living_part_6      
**Variable description**: Indicator of whether the participant is currently married or is currently living with a spouse or a partner in a common household.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not married or living with partner   
1 | Currently married or living with partner  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```   


# Number of people in household subdomain

### **Variable label**: Number people in household  
**Variable name**: sdc_num_hh_people_0      
**Variable description**: Number of people currently living in the same household, including the participant.    
**Value type**: integer      
**Variable unit**: individuals  
**Category coding**: N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Number people in household  
**Variable name**: sdc_num_hh_people_1    
**Variable description**: Number of people currently living in the same household, including the participant.    
**Value type**: integer      
**Variable unit**: individuals  
**Category coding**: N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Number people in household  
**Variable name**: sdc_num_hh_people_2    
**Variable description**: Number of people currently living in the same household, including the participant.    
**Value type**: integer      
**Variable unit**: individuals  
**Category coding**: N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

``` 
### **Variable label**: Number people in household  
**Variable name**: sdc_num_hh_people_3    
**Variable description**: Number of people currently living in the same household, including the participant.    
**Value type**: integer      
**Variable unit**: individuals  
**Category coding**: N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

``` 
### **Variable label**: Number people in household  
**Variable name**: sdc_num_hh_people_4    
**Variable description**: Number of people currently living in the same household, including the participant.    
**Value type**: integer      
**Variable unit**: individuals  
**Category coding**: N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

``` 
### **Variable label**: Number children in household  
**Variable name**: sdc_num_hh_children_0    
**Variable description**: Number of children currently living in the same household as the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Number children in household  
**Variable name**: sdc_num_hh_children_1     
**Variable description**: Number of children currently living in the same household as the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Number of children in household   
**Variable name**: sdc_num_hh_children_4  
**Variable description**: Number of children currently living in the same household as the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
### **Variable label**: Number of children 
**Variable name**: sdc_num_children_0  
**Variable description**: Number of children (biological or adopted).    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```    
### **Variable label**: Number of children  
**Variable name**: sdc_num_children_1  
**Variable description**: Number of children (biological or adopted).    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```   
### **Variable label**: Number of children   
**Variable name**: sdc_num_children_dich_4  
**Variable description**: Number of children (biological or adopted).    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```    
### **Variable label**: Participant has children (biological or adopted) 
**Variable name**: sdc_children_dich_0  
**Variable description**: Indicator of wether the participant has any children (biological or adopted) or not.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | No  
1 | Yes 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```    
### **Variable label**: Participant has children (biological or adopted)  
**Variable name**: sdc_children_1   
**Variable description**: Indicator of wether the participant has any children (biological or adopted) or not.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | No  
1 | Yes

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  
