---
title: "Sociodemographic characteristics LASA2"
output: html_document
---
# Connecting with Opal data server
## Login to server and assign study data
```{r, echo=FALSE}
#Load Opal R library
library(opal)
# Create an opal object with the login information
erasmus_opal <- opal.login()
#Login to Opal server and assign the content of the LASA table(s) to your RStudio environment
# LASA2B
opal.assign.table.tibble(erasmus_opal, 'LASA2B', 'LASA.LASA2B',variables = list('bage',"sex","bmarst","aeducat","bpartst","bpartner","bretired","bjob1",'binccat','bjobl1'))
LASA2B <- opal.execute(erasmus_opal,'LASA2B')

# LASA2F
opal.assign.table.tibble(erasmus_opal, 'LASA2F', 'LASA.LASA2F', variables=list('fage','sex','fmarst','aeducat','fpartner','fjob1','finccat','fretired','fjobc')) 
LASA2F<- opal.execute(erasmus_opal,'LASA2F')

# LASA2G
opal.assign.table.tibble(erasmus_opal,'LASA2G','LASA.LASA1G',variables=list('gage','sex','gmarst','aeducat','gpartner','gjob1','gretired','ginccat','gjobc')) 
LASA2G <- opal.execute(erasmus_opal,'LASA2G')

# LASA2H
opal.assign.table.tibble(erasmus_opal, 'LASA2H', 'LASA.LASA2H', variables= list('hage', 'sex', 'hmarst', 'aeducat', 'hpartner', 'hjob1', 'hretired', 'hinccat','hjobc')) 
LASA2H <- opal.execute(erasmus_opal,'LASA2H')


```
## Assign participant id as first column of your harmonized dataframes
```{r, echo=FALSE}
sdc_LASA2_0 <- data.frame(id = LASA2B$id)
sdc_LASA2_1 <- data.frame(id = LASA2F$id)
sdc_LASA2_2 <- data.frame(id = LASA2G$id)
sdc_LASA2_3 <- data.frame(id = LASA2H$id)

```
## When you are done with your work, logout of Opal server
```{r, echo=FALSE}
opal.logout(erasmus_opal) 
```

# Table of Contents
1. [Age and sex subdomain](#age-and-sex-subdomain)
2. [Employment and retirement subdomain](#employment-and-retirement-subdomain)
3. [Education and income subdomain](#education-and-income-subdomain)
4. [Marital status subdomain](#marital-status-subdomain)
5. [Number of people in household subdomain](#number-of-people-in-household-subdomain)

# Age and sex subdomain

### **Variable label**: Age of participant   
**Variable name**: sdc_age_0      
**Variable description**: Age of the participant.      
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   age is in decimal and was truncated to make it integer.  
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_0$sdc_age_0 <-  as.integer(LASA2B$bage)
```  
**Validation script**:  
```{r, echo=TRUE}
summary(sdc_LASA2_0$sdc_age_0)
summary(LASA2B$bage)
``` 
### **Variable label**: Age of participant   
**Variable name**: sdc_age_1       
**Variable description**: Age of the participant.      
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   age is in decimal and was truncated to make it integer.
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_1$sdc_age_1 <-  as.integer(LASA2F$fage)
``` 
**Validation script**:  
```{r, echo=TRUE}
summary(sdc_LASA2_1$sdc_age_1)
summary(LASA2F$fage)
``` 
### **Variable label**: Age of participant   
**Variable name**: sdc_age_2     
**Variable description**: Age of the participant.      
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   age is in decimal and was truncated to make it integer.  
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_2$sdc_age_2 <-  as.integer(LASA2G$gage)
```  
**Validation script**:  
```{r, echo=TRUE}
summary(sdc_LASA2_2$sdc_age_2)
summary(LASA2G$gage)
``` 
### **Variable label**: Age of participant   
**Variable name**: sdc_age_3     
**Variable description**: Age of the participant.     
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   age is in decimal and was truncated to make it integer.  
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_3$sdc_age_3 <-  as.integer(LASA2H$hage)
```  
**Validation script**:  
```{r, echo=TRUE}
summary(sdc_LASA2_3$sdc_age_3)
summary(LASA2H$hage)
``` 
### **Variable label**: Age of participant   
**Variable name**: sdc_age_4       
**Variable description**: Age of the participant.      
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Age of participant   
**Variable name**: sdc_age_5     
**Variable description**: Age of the participant.      
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Age of participant   
**Variable name**: sdc_age_6     
**Variable description**: Age of the participant.      
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Gender of participant   
**Variable name**: sdc_gender_0       
**Variable description**: Gender of the participant.      
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Male   
1 | Female   

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_0$sdc_gender_0 <- recode(as.integer(LASA2B$sex),'1'=0L,'2'=1L)
```  
**Validation script**:  
```{r, echo=TRUE}
summ(as.factor(sdc_LASA2_0$sdc_gender_0))

attributes(LASA2B$sex)
A<-addmargins(table(sdc_LASA2_0$sdc_gender_0,LASA2B$sex,useNA = "always"))
colnames(A)<-c(names(attributes(LASA2B$sex)[[9]]),"NA","SUM")
as.data.frame.array(A,row.names = c("Male","Female","NA","SUM"))
``` 
### **Variable label**: Gender of participant   
**Variable name**: sdc_gender_1       
**Variable description**: Gender of the participant.      
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Male   
1 | Female   

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_1$sdc_gender_1 <- recode(as.integer(LASA2F$sex),'1'=0L,'2'=1L)
```  
**Validation script**:  
```{r, echo=TRUE}
summ(as.factor(sdc_LASA2_1$sdc_gender_1))

attributes(LASA2F$sex)
A<-addmargins(table(sdc_LASA2_1$sdc_gender_1,LASA2F$sex,useNA = "always"))
colnames(A)<-c(names(attributes(LASA2F$sex)[[9]]),"NA","SUM")
as.data.frame.array(A,row.names = c("Male","Female","NA","SUM"))
``` 
### **Variable label**: Gender of participant   
**Variable name**: sdc_gender_2       
**Variable description**: Gender of the participant.      
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Male   
1 | Female   

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_2$sdc_gender_2 <- recode(as.integer(LASA2G$sex),'1'=0L,'2'=1L)
``` 
**Validation script**:  
```{r, echo=TRUE}
summ(as.factor(sdc_LASA2_2$sdc_gender_2))

attributes(LASA2G$sex)
A<-addmargins(table(sdc_LASA2_2$sdc_gender_2,LASA2G$sex,useNA = "always"))
colnames(A)<-c(names(attributes(LASA2G$sex)[[9]]),"NA","SUM")
as.data.frame.array(A,row.names = c("Male","Female","NA","SUM"))
``` 
### **Variable label**: Gender of participant   
**Variable name**: sdc_gender_3       
**Variable description**: Gender of the participant.      
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Male   
1 | Female   

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_3$sdc_gender_3 <- recode(as.integer(LASA2H$sex),'1'=0L,'2'=1L)
```  
**Validation script**:  
```{r, echo=TRUE}
summ(as.factor(sdc_LASA2_3$sdc_gender_3))

attributes(LASA2H$sex)
A<-addmargins(table(sdc_LASA2_3$sdc_gender_3,LASA2H$sex,useNA = "always"))
colnames(A)<-c(names(attributes(LASA2H$sex)[[9]]),"NA","SUM")
as.data.frame.array(A,row.names = c("Male","Female","NA","SUM"))
``` 
### **Variable label**: Gender of participant   
**Variable name**: sdc_gender_4       
**Variable description**: Gender of the participant.      
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Male   
1 | Female   

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Gender of participant   
**Variable name**: sdc_gender_5       
**Variable description**: Gender of the participant.      
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Male   
1 | Female   

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Gender of participant   
**Variable name**: sdc_gender_6       
**Variable description**: Gender of the participant.      
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Male   
1 | Female   

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
# Employment and retirement subdomain

### **Variable label**: Employment status   
**Variable name**: sdc_employ_0       
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in paid employment   
1 | Currently in paid employment

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_0$sdc_employ_0 <- recode(as.integer(LASA2B$bjob1),'1'=0L,'2'=1L, .default = NA_integer_ )
```  
**Validation script**:  
```{r, echo=TRUE}
summ(as.factor(sdc_LASA2_0$sdc_employ_0))

attributes(LASA2B$bjob1)
A<-addmargins(table(sdc_LASA2_0$sdc_employ_0,LASA2B$bjob1,useNA = "always"))
colnames(A)<-c(names(attributes(LASA2B$bjob1)[[9]]),"NA","SUM")
as.data.frame.array(A,row.names = c("Currently not in paid employment","Currently in paid employment","NA","SUM"))
``` 
### **Variable label**: Employment status   
**Variable name**: sdc_employ_1    
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in paid employment   
1 | Currently in paid employment  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_1$sdc_employ_1 <- recode(as.integer(LASA2F$fjob1),'1'=0L,'2'=1L, .default = NA_integer_ )
```  
**Validation script**:  
```{r, echo=TRUE}
summ(as.factor(sdc_LASA2_1$sdc_employ_1))

attributes(LASA2F$fjob1)
A<-addmargins(table(sdc_LASA2_1$sdc_employ_1,LASA2F$fjob1,useNA = "always"))
colnames(A)<-c(names(attributes(LASA2F$fjob1)[[9]]),"NA","SUM")
as.data.frame.array(A,row.names = c("Currently not in paid employment","Currently in paid employment","NA","SUM"))
```
### **Variable label**: Employment status   
**Variable name**: sdc_employ_2    
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in paid employment   
1 | Currently in paid employment   

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_2$sdc_employ_2 <- recode(as.integer(LASA2G$gjob1),'1'=0L,'2'=1L, .default = NA_integer_ )
```  
**Validation script**:  
```{r, echo=TRUE}
summ(as.factor(sdc_LASA2_2$sdc_employ_2))

attributes(LASA2F$fjob1)
A<-addmargins(table(sdc_LASA2_2$sdc_employ_2,LASA2G$gjob1,useNA = "always"))
colnames(A)<-c(names(attributes(LASA2G$gjob1)[[9]]),"NA","SUM")
as.data.frame.array(A,row.names = c("Currently not in paid employment","Currently in paid employment","NA","SUM"))
```
### **Variable label**: Employment status   
**Variable name**: sdc_employ_3    
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in paid employment   
1 | Currently in paid employment   

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_3$sdc_employ_3 <- recode(as.integer(LASA2H$hjob1),'1'=0L,'2'=1L, .default = NA_integer_ )
``` 
**Validation script**:  
```{r, echo=TRUE}
summ(as.factor(sdc_LASA2_3$sdc_employ_3))

attributes(LASA2F$fjob1)
A<-addmargins(table(sdc_LASA2_3$sdc_employ_3,LASA2H$hjob1,useNA = "always"))
colnames(A)<-c(names(attributes(LASA2H$hjob1)[[9]][2:4]),"NA","SUM")
as.data.frame.array(A,row.names = c("Currently not in paid employment","Currently in paid employment","NA","SUM"))
```
### **Variable label**: Employment status   
**Variable name**: sdc_employ_4    
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in paid employment   
1 | Currently in paid employment   

**Harmonization status**:  impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Employment status   
**Variable name**: sdc_employ_5    
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in paid employment   
1 | Currently in paid employment   

**Harmonization status**:  impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Employment status   
**Variable name**: sdc_employ_6    
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in paid employment   
1 | Currently in paid employment   

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Retirement status   
**Variable name**: sdc_retire_0     
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in retirement   
1 | Currently in retirement   

**Harmonization status**:  complete  
**Harmonization comment**:  Categories partly retired, completely retired, and >= 65 years were coded to currently in retirement.    
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_0$sdc_retired_0 <- ifelse(as.integer(LASA2B$bretired)==1 | (as.integer(LASA2B$bretired)==-2 & as.integer(LASA2B$bjob1)>0),0L, ifelse(as.integer(LASA1B$bretired)==-5 | as.integer(LASA1B$bretired)==2 | as.integer(LASA1B$bretired)==3,1L,NA))
```  
**Validation script**:  
```{r, echo=TRUE}
summ(as.factor(sdc_LASA2_0$sdc_retired_0))

attributes(LASA2B$bretired)
A<-addmargins(table(sdc_LASA2_0$sdc_retired_0,LASA2B$bretired,useNA = "always"))
#colnames(A)<-c(names(attributes(LASA2B$bretired)[[9]]),"NA","SUM")
#as.data.frame.array(A,row.names = c("Currently not in retirement","Currently in retirement","NA","SUM"))
```  
**Correction script**:  
```{r, echo=TRUE}
sdc_LASA2_0$sdc_retired_0 <- ifelse(as.integer(LASA2B$bretired)==1 | (as.integer(LASA2B$bretired)==-2 & as.integer(LASA2B$bjob1)>0),0L, ifelse(as.integer(LASA2B$bretired)==-5 | as.integer(LASA2B$bretired)==2 | as.integer(LASA2B$bretired)==3,1L,NA))
``` 

### **Variable label**: Retirement status   
**Variable name**: sdc_retire_1     
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in retirement   
1 | Currently in retirement   

**Harmonization status**:  complete  
**Harmonization comment**:    Categories partly retired, completely retired, and >= 65 years were coded to currently in retirement.  
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_1$sdc_retired_1 <- ifelse(as.integer(LASA2F$fretired)== 1 | (as.integer(LASA2F$fretired)== -2 & as.integer(LASA2F$fjobc)> -2 | as.integer(LASA2F$fretired)== -2 & as.integer(LASA2F$fjob1)> 0), 0L, ifelse(as.integer(LASA2F$fretired)== -5 | as.integer(LASA2F$fretired)== 2 | as.integer(LASA2F$fretired)== 3, 1L,NA))
```  
**Validation script**:  
```{r, echo=TRUE}
summ(as.factor(sdc_LASA2_1$sdc_retired_1))

A<-addmargins(table(sdc_LASA2_1$sdc_retired_1,LASA2F$fretired,useNA = "always"))
colnames(A)<-c(names(attributes(LASA2F$fretired)[[9]][c(4,2,5:7)]),"NA","SUM")
as.data.frame.array(A,row.names = c("Currently not in retirement","Currently in retirement","NA","SUM"))
``` 
### **Variable label**: Retirement status   
**Variable name**: sdc_retire_2     
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in retirement   
1 | Currently in retirement   

**Harmonization status**:  complete  
**Harmonization comment**:    Categories partly retired, completely retired, and >= 65 years were coded to currently in retirement.  
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_2$sdc_retired_2 <- ifelse(as.integer(LASA2G$gretired)== 1 | (as.integer(LASA2G$gretired)== -2 & as.integer(LASA2G$gjobc)> -2 | as.integer(LASA2G$gretired)== -2 & as.integer(LASA2G$gjob1)> 0), 0L, ifelse(as.integer(LASA2G$gretired)== -5 | as.integer(LASA2G$gretired)== 2 | as.integer(LASA2G$gretired)== 3, 1L,NA))
```  
### **Variable label**: Retirement status   
**Variable name**: sdc_retire_3     
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in retirement   
1 | Currently in retirement   

**Harmonization status**:  complete  
**Harmonization comment**:    Categories partly retired, completely retired, and >= 65 years were coded to currently in retirement.  
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_3$sdc_retired_3 <- ifelse(as.integer(LASA2H$hretired)== 1 | (as.integer(LASA2H$hretired)== -2 & as.integer(LASA2H$hjobc)> -2 | as.integer(LASA2H$hretired)== -2 & as.integer(LASA2H$hjob1)> 0), 0L, ifelse(as.integer(LASA2H$hretired)== -5 | as.integer(LASA2H$hretired)== 2 | as.integer(LASA2H$hretired)== 3, 1L,NA))
```  
### **Variable label**: Retirement status   
**Variable name**: sdc_retire_4     
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in retirement   
1 | Currently in retirement   

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Retirement status   
**Variable name**: sdc_retire_5     
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in retirement   
1 | Currently in retirement   

**Harmonization status**:  impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Retirement status   
**Variable name**: sdc_retire_6      
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in retirement   
1 | Currently in retirement   

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Retirement age   
**Variable name**: sdc_retire_age_0      
**Variable description**: Age of the participant at retirement.  
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Retirement age    
**Variable name**: sdc_retire_age_1    
**Variable description**: Age of the participant at retirement.  
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Retirement age    
**Variable name**: sdc_retire_age_2    
**Variable description**: Age of the participant at retirement.    
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  

# Education and income subdomain

### **Variable label**: Highest level of education completed (ISCED 2011)    
**Variable name**: sdc_highest_edu_0       
**Variable description**: Highest level of education completed by the participant in accordance with the International Standard Classification of Education (ISCED 2011).       
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Lower secondary or less (ISCED 0-2)  
2 | Upper secondary (ISCED 3)
3 | Post-secondary non-tertiary education or short-cycle tertiary education (ISCED 4,5)
4 | Bachelor,master,doctoral or equivalent (ISCED 6,7,8)

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_0$sdc_highest_edu_0 <- recode(as.integer(LASA2B$aeducat), '1'=1L, '2'=1L, '3'=1L, '4'=1L, '5'=2L, '6'=2L, '7'=4L, '8'=4L, '9'=4L, .default=NA_integer_)
```  
### **Variable label**: Highest level of education completed (ISCED 2011)    
**Variable name**: sdc_highest_edu_1     
**Variable description**: Highest level of education completed by the participant in accordance with the International Standard Classification of Education (ISCED 2011).     
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Lower secondary or less (ISCED 0-2)  
2 | Upper secondary (ISCED 3)
3 | Post-secondary non-tertiary education or short-cycle tertiary education (ISCED 4,5)
4 | Bachelor,master,doctoral,or equivalent (ISCED 6,7,8)

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_1$sdc_highest_edu_1 <- recode(as.integer(LASA2F$aeducat), '1'=1L, '2'=1L, '3'=1L, '4'=1L, '5'=2L, '6'=2L, '7'=4L, '8'=4L, '9'=4L, .default=NA_integer_)
```  
### **Variable label**: Highest level of education completed (ISCED 2011)    
**Variable name**: sdc_highest_edu_2     
**Variable description**: Highest level of education completed by the participant in accordance with the International Standard Classification of Education (ISCED 2011).     
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Lower secondary or less (ISCED 0-2)  
2 | Upper secondary (ISCED 3)
3 | Post-secondary non-tertiary education or short-cycle tertiary education (ISCED 4,5)
4 | Bachelor,master,doctoral,or equivalent (ISCED 6,7,8)

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_2$sdc_highest_edu_2 <- recode(as.integer(LASA2G$aeducat), '1'=1L, '2'=1L, '3'=1L, '4'=1L, '5'=2L, '6'=2L, '7'=4L, '8'=4L, '9'=4L, .default=NA_integer_)

```  
### **Variable label**: Highest level of education completed (ISCED 2011)    
**Variable name**: sdc_highest_edu_3     
**Variable description**: Highest level of education completed by the participant in accordance with the International Standard Classification of Education (ISCED 2011).     
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Lower secondary or less (ISCED 0-2)  
2 | Upper secondary (ISCED 3)
3 | Post-secondary non-tertiary education or short-cycle tertiary education (ISCED 4,5)
4 | Bachelor,master,doctoral,or equivalent (ISCED 6,7,8)

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_3$sdc_highest_edu_3 <- recode(as.integer(LASA2H$aeducat), '1'=1L, '2'=1L, '3'=1L, '4'=1L, '5'=2L, '6'=2L, '7'=4L, '8'=4L, '9'=4L, .default=NA_integer_)

```  
### **Variable label**: Highest level of education completed (ISCED 2011)    
**Variable name**: sdc_highest_edu_4     
**Variable description**: Highest level of education completed by the participant in accordance with the International Standard Classification of Education (ISCED 2011).     
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Lower secondary or less (ISCED 0-2)  
2 | Upper secondary (ISCED 3)
3 | Post-secondary non-tertiary education or short-cycle tertiary education (ISCED 4,5)
4 | Bachelor,master,doctoral,or equivalent (ISCED 6,7,8)

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Post-secondary education    
**Variable name**: sdc_postsec_edu_0       
**Variable description**: Indicator of whether the participant completed highschool or post-secondary education.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Upper secondary or less (ISCED 0-3)
1 | Post-secondary non-tertiary education or more (ISCED 4-8)  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_0$sdc_postsec_edu_0 <- recode(as.integer(LASA2B$aeducat), '1'=0L, '2'=0L, '3'=0L, '4'=0L, '5'=0L, '6'=0L, '7'=1L, '8'=1L, '9'=1L, .default=NA_integer_)

```  
### **Variable label**: Post-secondary education    
**Variable name**: sdc_postsec_edu_1     
**Variable description**: Indicator of whether the participant completed highschool or post-secondary education.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Upper secondary or less (ISCED 0-3)
1 | Post-secondary non-tertiary education or more (ISCED 4-8)    

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_1$sdc_postsec_edu_1 <- recode(as.integer(LASA2F$aeducat), '1'=0L, '2'=0L, '3'=0L, '4'=0L, '5'=0L, '6'=0L, '7'=1L, '8'=1L, '9'=1L, .default=NA_integer_)

```  
### **Variable label**: Post-secondary education    
**Variable name**: sdc_postsec_edu_2     
**Variable description**: Indicator of whether the participant completed highschool or post-secondary education.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Upper secondary or less (ISCED 0-3)
1 | Post-secondary non-tertiary education or more (ISCED 4-8)    

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_2$sdc_postsec_edu_2 <- recode(as.integer(LASA2G$aeducat), '1'=0L, '2'=0L, '3'=0L, '4'=0L, '5'=0L, '6'=0L, '7'=1L, '8'=1L, '9'=1L, .default=NA_integer_)

```  
### **Variable label**: Post-secondary education    
**Variable name**: sdc_postsec_edu_3     
**Variable description**: Indicator of whether the participant completed highschool or post-secondary education.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Upper secondary or less (ISCED 0-3)
1 | Post-secondary non-tertiary education or more (ISCED 4-8)    

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_3$sdc_postsec_edu_3 <- recode(as.integer(LASA2H$aeducat), '1'=0L, '2'=0L, '3'=0L, '4'=0L, '5'=0L, '6'=0L, '7'=1L, '8'=1L, '9'=1L, .default=NA_integer_)

```  
### **Variable label**: Post-secondary education    
**Variable name**: sdc_postsec_edu_4     
**Variable description**: Indicator of whether the participant completed highschool or post-secondary education.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Upper secondary or less (ISCED 0-3)
1 | Post-secondary non-tertiary education or more (ISCED 4-8)    

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Net annual household income    
**Variable name**: sdc_income_0       
**Variable description**: Indicator of whether the net annual household income is above or below the country-specific net mean household income.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income    

**Harmonization status**:  
**Harmonization comment**:    LASA2 wave A/B (baseline) collected in 2002-2003. mean net household income for those years in Netherlands not available by OECD. 2000 (20 067) and 2005 (23 895) data available so average was taken. Study-specific categories are ranges of income per month. mapping to the DataSchema variable (above or below country-specific net mean household income) was done considering the mean of each range category.
According to LASA notes, 1 Dutch Guilder = 0.45 Euro, this is the conversion that was used for harmonization. 
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_0$sdc_income_0 <- ifelse( -1 < (as.integer(LASA2B$binccat)) & (as.integer(LASA2B$binccat)) < 11,0L,
                                    ifelse((as.integer(LASA2B$binccat)) > 10, 1L, NA))

```  
### **Variable label**: Net annual household income    
**Variable name**: sdc_income_1       
**Variable description**: Indicator of whether the net annual household income is above or below the country-specific net mean household income.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income    

**Harmonization status**:  complete  
**Harmonization comment**:   LASA2 wave F (first followup) collected in 2005-2006. mean net household income for 2005 in Netherlands is 23 895 Euro according to OECD. Study-specific categories are ranges of income per month. mapping to the DataSchema variable (above or below country-specific net mean household income) was done considering the mean of each range category.
According to LASA notes, 1 Dutch Guilder = 0.45 Euro, this is the conversion that was used for harmonization.  
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_1$sdc_income_1 <- ifelse( -1 < (as.integer(LASA2F$finccat)) & (as.integer(LASA2F$finccat)) < 11,0L,
                                    ifelse((as.integer(LASA2F$finccat)) > 10, 1L, NA))

```    
### **Variable label**: Net annual household income    
**Variable name**: sdc_income_2       
**Variable description**: Indicator of whether the net annual household income is above or below the country-specific net mean household income.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income    

**Harmonization status**:  complete  
**Harmonization comment**:   LASA2 wave G (second followup) collected in 2008-2009. mean net household income for 2008 in Netherlands is 24 883 according to OECD. Study-specific categories are ranges of income per month. mapping to the DataSchema variable (above or below country-specific net mean household income) was done considering the mean of each range category.
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_2$sdc_income_2 <- ifelse( -1 < (as.integer(LASA2G$ginccat)) & (as.integer(LASA2G$ginccat)) < 11,0L,
                                    ifelse((as.integer(LASA2G$ginccat)) > 10, 1L, NA))

```   
### **Variable label**: Net annual household income    
**Variable name**: sdc_income_3       
**Variable description**: Indicator of whether the net annual household income is above or below the country-specific net mean household income.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income    

**Harmonization status**:  
**Harmonization comment**:   LASA1 wave H (third followup) collected in 2011-2012. mean net household income for 2012 in Netherlands is 25 100 according to OECD (data not available for 2011 and in 2010 income was also 25 100 according to OECD). Study-specific categories are ranges of income per month. mapping to the DataSchema variable (above or below country-specific net mean household income) was done considering the mean of each range category.  
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_3$sdc_income_3 <- ifelse( -1 < (as.integer(LASA2H$hinccat)) & (as.integer(LASA2H$hinccat)) < 11,0L,
                                    ifelse((as.integer(LASA2H$hinccat)) > 10, 1L, NA))

```   
### **Variable label**: Net annual household income    
**Variable name**: sdc_income_4       
**Variable description**: Indicator of whether the net annual household income is above or below the country-specific net mean household income.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income    

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```   
### **Variable label**: Net annual household income    
**Variable name**: sdc_income_5       
**Variable description**: Indicator of whether the net annual household income is above or below the country-specific net mean household income.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income    

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Net annual household income    
**Variable name**: sdc_income_6       
**Variable description**: Indicator of whether the net annual household income is above or below the country-specific net mean household income.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income    

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
# Marital status subdomain

### **Variable label**: Civil status    
**Variable name**: sdc_civstat_0      
**Variable description**: Indicator of the participant's current civil status.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently single or unmarried   
1 | Currently married or living with partner
2 | Currently divorced or separated
3 | Currently widowed  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_0$sdc_civstat_0 <- recode(as.integer(LASA2B$bmarst),'5'=1L,'1'=0L,'2'=1L,'3'=2L,'4'=3L, .default = NA_integer_)

```  
### **Variable label**: Civil status    
**Variable name**: sdc_civstat_1      
**Variable description**: Indicator of the participant's current civil status.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently single or unmarried   
1 | Currently married or living with partner
2 | Currently divorced or separated
3 | Currently widowed  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_1$sdc_civstat_1 <- recode(as.integer(LASA2F$marst),'5'=1L,'1'=0L,'2'=1L,'3'=2L,'4'=3L, .default = NA_integer_)

```   
### **Variable label**: Civil status    
**Variable name**: sdc_civstat_2      
**Variable description**: Indicator of the participant's current civil status.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently single or unmarried   
1 | Currently married or living with partner
2 | Currently divorced or separated
3 | Currently widowed  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_2$sdc_civstat_2 <- recode(as.integer(LASA2G$gmarst),'5'=1L,'1'=0L,'2'=1L,'3'=2L,'4'=3L, .default = NA_integer_)

```   
### **Variable label**: Civil status    
**Variable name**: sdc_civstat_3        
**Variable description**: Indicator of the participant's current civil status.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently single or unmarried   
1 | Currently married or living with partner
2 | Currently divorced or separated
3 | Currently widowed  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_3$sdc_civstat_3 <- recode(as.integer(LASA2H$hmarst),'5'=1L,'1'=0L,'2'=1L,'3'=2L,'4'=3L, .default = NA_integer_)

```  
### **Variable label**: Civil status    
**Variable name**: sdc_civstat_4      
**Variable description**: Indicator of the participant's current civil status.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently single or unmarried   
1 | Currently married or living with partner
2 | Currently divorced or separated
3 | Currently widowed  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```   
### **Variable label**: Civil status    
**Variable name**: sdc_civstat_5      
**Variable description**: Indicator of the participant's current civil status.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently single or unmarried   
1 | Currently married or living with partner
2 | Currently divorced or separated
3 | Currently widowed  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```   
### **Variable label**: Civil status    
**Variable name**: sdc_civstat_6      
**Variable description**: Indicator of the participant's current civil status.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently single or unmarried   
1 | Currently married or living with partner
2 | Currently divorced or separated
3 | Currently widowed  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```    
### **Variable label**: Married or living with partner  
**Variable name**: sdc_livstat_0      
**Variable description**: Indicator of whether the participant is currently married or is currently living with a spouse or a partner in a common household.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not married or living with partner   
1 | Currently married or living with partner  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_0$sdc_livstat_0 <- recode(as.integer(LASA2B$bpartner),'0'=0L,'1'=1L,'2'=0L)

```  
### **Variable label**: Married or living with partner  
**Variable name**: sdc_livstat_1      
**Variable description**: Indicator of whether the participant is currently married or is currently living with a spouse or a partner in a common household.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not married or living with partner   
1 | Currently married or living with partner  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_1$sdc_livstat_1 <- recode(as.integer(LASA2F$fpartner),'0'=0L,'1'=1L,'2'=0L)

```   
### **Variable label**: Married or living with partner  
**Variable name**: sdc_livstat_2      
**Variable description**: Indicator of whether the participant is currently married or is currently living with a spouse or a partner in a common household.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not married or living with partner   
1 | Currently married or living with partner  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_2$sdc_livstat_2 <- recode(as.integer(LASA2G$gpartner),'0'=0L,'1'=1L,'2'=0L)

```  
### **Variable label**: Married or living with partner  
**Variable name**: sdc_livstat_3      
**Variable description**: Indicator of whether the participant is currently married or is currently living with a spouse or a partner in a common household.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not married or living with partner   
1 | Currently married or living with partner  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_LASA2_3$sdc_livstat_3 <- recode(as.integer(LASA2H$hpartner),'0'=0L,'1'=1L,'2'=0L)

```  
### **Variable label**: Married or living with partner  
**Variable name**: sdc_livstat_4      
**Variable description**: Indicator of whether the participant is currently married or is currently living with a spouse or a partner in a common household.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not married or living with partner   
1 | Currently married or living with partner  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Married or living with partner  
**Variable name**: sdc_livstat_5      
**Variable description**: Indicator of whether the participant is currently married or is currently living with a spouse or a partner in a common household.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not married or living with partner   
1 | Currently married or living with partner  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```    
### **Variable label**: Married or living with partner  
**Variable name**: sdc_livstat_6      
**Variable description**: Indicator of whether the participant is currently married or is currently living with a spouse or a partner in a common household.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not married or living with partner   
1 | Currently married or living with partner  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```   


# Number of people in household subdomain

### **Variable label**: Number people in household  
**Variable name**: sdc_num_pplhh_0      
**Variable description**: Number of people currently living in the same household, including the participant.    
**Value type**: integer      
**Variable unit**: individuals  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Number people in household  
**Variable name**: sdc_num_pplhh_1    
**Variable description**: Number of people currently living in the same household, including the participant.    
**Value type**: integer      
**Variable unit**: individuals  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Number people in household  
**Variable name**: sdc_num_pplhh_2    
**Variable description**: Number of people currently living in the same household, including the participant.    
**Value type**: integer      
**Variable unit**: individuals  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


``` 
### **Variable label**: Number people in household  
**Variable name**: sdc_num_pplhh_3    
**Variable description**: Number of people currently living in the same household, including the participant.    
**Value type**: integer      
**Variable unit**: individuals  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


``` 
### **Variable label**: Number people in household  
**Variable name**: sdc_num_pplhh_4    
**Variable description**: Number of people currently living in the same household, including the participant.    
**Value type**: integer      
**Variable unit**: individuals  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}


``` 
### **Variable label**: Number children in household  
**Variable name**: sdc_num_childhh_0    
**Variable description**: Number of children (biological or adopted) currently living in the same household as the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Number children in household  
**Variable name**: sdc_num_childhh_1     
**Variable description**: Number of children (biological or adopted) currently living in the same household as the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:   impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Number children in household  
**Variable name**: sdc_num_childhh_2     
**Variable description**: Number of children (biological or adopted) currently living in the same household as the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Number children in household  
**Variable name**: sdc_num_childhh_3     
**Variable description**: Number of children (biological or adopted) currently living in the same household as the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Number of children in household   
**Variable name**: sdc_num_childhh_4  
**Variable description**: Number of children (biological or adopted) currently living in the same household as the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Number of children 
**Variable name**: sdc_num_child_0  
**Variable description**: Number of children (biological or adopted) of the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```    
### **Variable label**: Number of children  
**Variable name**: sdc_num_child_1  
**Variable description**: Number of children (biological or adopted) of the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:  impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```   
### **Variable label**: Number of children  
**Variable name**: sdc_num_child_2  
**Variable description**: Number of children (biological or adopted) of the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:  impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```   
### **Variable label**: Number of children  
**Variable name**: sdc_num_child_3  
**Variable description**: Number of children (biological or adopted) of the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```   
### **Variable label**: Number of children   
**Variable name**: sdc_num_child_4  
**Variable description**: Number of children (biological or adopted) of the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```    
### **Variable label**: Children (biological or adopted) 
**Variable name**: sdc_child_0  
**Variable description**: Indicator of wether the participant has any children (biological or adopted) or not.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Does not have children  
1 | Does have children

**Harmonization status**:  impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```    
### **Variable label**: Children (biological or adopted)  
**Variable name**: sdc_child_1   
**Variable description**: Indicator of wether the participant has any children (biological or adopted) or not.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Does not have children  
1 | Does have children

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Children (biological or adopted)  
**Variable name**: sdc_child_2   
**Variable description**: Indicator of wether the participant has any children (biological or adopted) or not.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Does not have children  
1 | Does have children

**Harmonization status**:  impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Children (biological or adopted)  
**Variable name**: sdc_child_3   
**Variable description**: Indicator of wether the participant has any children (biological or adopted) or not.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Does not have children  
1 | Does have children

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Children (biological or adopted)  
**Variable name**: sdc_child_4   
**Variable description**: Indicator of wether the participant has any children (biological or adopted) or not.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Does not have children  
1 | Does have children

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  