---
title: "Sociodemographic characteristics DataSchema"
output: html_document
---



```{r, echo=TRUE}
library(epiDisplay)
library(dplyr)
library(data.table)


# Connecting with Opal data server
## Login to server and assign study data
#Load Opal R library
library(opal)
# Create an opal object with the login information
erasmus_opal <- opal.login()
#Login to Opal server and assign the content of the GLOBE table(s) to your RStudio environment
# GLOBE1991
opal.assign.table.tibble(erasmus_opal, 'GLOBE1991', 'GLOBE.GLOBE1991',variables = list('v352','v244','SEVMv812',"v279","v307","SEGVv448","v157","SEVMv818","v338","v335","v351","Gender_overall","SEGVv639","SEVMv817","v244","v257","SEVMv772","v247"))

GLOBE1991 <- opal.execute(erasmus_opal,'GLOBE1991')

# GLOBE1997
opal.assign.table.tibble(erasmus_opal, 'GLOBE1997', 'GLOBE.GLOBE1997',variables = list("r44b","g1b","g1a","r44a","g26a","r62a","r45a","g2a","r45b","g2b","r56a","g20a"))

GLOBE1997 <- opal.execute(erasmus_opal,'GLOBE1997')

# GLOBE2004
opal.assign.table.tibble(erasmus_opal, 'GLOBE2004', 'GLOBE.GLOBE2004',variables = list("w255","w254","w260","w277","w258","w259","w042","w243"))

GLOBE2004 <- opal.execute(erasmus_opal,'GLOBE2004')

# GLOBE2011
opal.assign.table.tibble(erasmus_opal, 'GLOBE2011', 'GLOBE.GLOBE2011',variables = list("v2_leeftijd","v1_geslacht","v9_opleiding_opl_1","v51_pers_won","v6_woons","v6_woons_and","v5_burger_staat","v67_inkomen","SEGVv639",'v7_werks'))

GLOBE2011 <- opal.execute(erasmus_opal,'GLOBE2011')

# GLOBE2014
opal.assign.table.tibble(erasmus_opal, 'GLOBE2014', 'GLOBE.GLOBE2014',variables = list('G14v2','G14v1','G14v5','G14v8other1','G14v8_opl1','G14v93','G14v5','G14v6','G14v89' ,'G14v10','G14v9',"G14v12"))

GLOBE2014 <- opal.execute(erasmus_opal,'GLOBE2014')

```
## Assign participant id as first column of your harmonized dataframes
```{r, echo=FALSE}
sdc_GLOBE_0 <- data.frame(id = GLOBE1991$id )
sdc_GLOBE_1 <- data.frame(id = GLOBE1997$id )
sdc_GLOBE_2 <- data.frame(id = GLOBE2004$id )
sdc_GLOBE_3 <- data.frame(id = GLOBE2011$id )
sdc_GLOBE_4 <- data.frame(id = GLOBE2014$id )
```

# Table of Contents
1. [Age and sex subdomain](#age-and-sex-subdomain)
2. [Employment and retirement subdomain](#employment-and-retirement-subdomain)
3. [Education and income subdomain](#education-and-income-subdomain)
4. [Marital status subdomain](#marital-status-subdomain)
5. [Number of people in household subdomain](#number-of-people-in-household-subdomain)

# Age and sex subdomain

### **Variable label**: Age of participant   
**Variable name**: sdc_age_0      
**Variable description**: Age of the participant.      
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_0$sdc_age_0<-GLOBE1991$v352

```  

### **Variable label**: Age of participant   
**Variable name**: sdc_age_1       
**Variable description**: Age of the participant.      
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   2 variables used for age. r44b and g1b  
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_1$sdc_age_1<-ifelse(!is.na(GLOBE1997$r44b),GLOBE1997$r44b,
                              ifelse(!is.na(GLOBE1997$g1b),GLOBE1997$g1b,NA))

```  
### **Variable label**: Age of participant   
**Variable name**: sdc_age_2     
**Variable description**: Age of the participant.      
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   w255  
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_2$sdc_age_2<-GLOBE2004$w255

```  
### **Variable label**: Age of participant   
**Variable name**: sdc_age_3     
**Variable description**: Age of the participant.     
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_3$sdc_age_3<-GLOBE2011$v2_leeftijd

```  
### **Variable label**: Age of participant   
**Variable name**: sdc_age_4       
**Variable description**: Age of the participant.      
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:   complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_4$sdc_age_4<-GLOBE2014$G14v2

```  
### **Variable label**: Age of participant   
**Variable name**: sdc_age_5     
**Variable description**: Age of the participant.      
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Age of participant   
**Variable name**: sdc_age_6     
**Variable description**: Age of the participant.      
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Gender of participant   
**Variable name**: sdc_gender_0       
**Variable description**: Gender of the participant.      
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Male   
1 | Female   

**Harmonization status**:  complete  
**Harmonization comment**:  According to the region, Gender_overall is the variable to be used instead of v351.  
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_1$sdc_gender_0<-GLOBE1991$Gender_overall
```  
### **Variable label**: Gender of participant   
**Variable name**: sdc_gender_1       
**Variable description**: Gender of the participant.      
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Male   
1 | Female   

**Harmonization status**:  complete  
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_1$sdc_gender_1<-ifelse(!is.na(GLOBE1997$g1a),GLOBE1997$g1a,
                              ifelse(!is.na(GLOBE1997$r44a),GLOBE1997$r44a,NA))
sdc_GLOBE_1$sdc_gender_1<-recode(sdc_GLOBE_1$sdc_gender_1, '1'=0L,'2'=1L)

```  
### **Variable label**: Gender of participant   
**Variable name**: sdc_gender_2       
**Variable description**: Gender of the participant.      
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Male   
1 | Female   

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_2$sdc_gender_2<-recode(as.integer(GLOBE2004$w254),'1'=0L,'2'=1L)
```  
### **Variable label**: Gender of participant   
**Variable name**: sdc_gender_3       
**Variable description**: Gender of the participant.      
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Male   
1 | Female   

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_3$sdc_gender_3<-recode(as.integer(GLOBE2011$v1_geslacht),'1'=1L,'2'=0L)

```  
### **Variable label**: Gender of participant   
**Variable name**: sdc_gender_4       
**Variable description**: Gender of the participant.      
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Male   
1 | Female   

**Harmonization status**:  complete
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_4$sdc_gender_4<-recode(as.integer(GLOBE2014$G14v1),'1'=1L,'2'=0L)
```  
### **Variable label**: Gender of participant   
**Variable name**: sdc_gender_5       
**Variable description**: Gender of the participant.      
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Male   
1 | Female   

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Gender of participant   
**Variable name**: sdc_gender_6       
**Variable description**: Gender of the participant.      
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Male   
1 | Female   

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
# Employment and retirement subdomain

### **Variable label**: Employment status   
**Variable name**: sdc_employ_0       
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in paid employment   
1 | Currently in paid employment

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_0$sdc_employ_0<-recode(as.integer(GLOBE1991$v247),'1'=1L,'2'=0L,'3'=0L,'4'=0L,'5'=0L,'6'=0L,'7'=0L,'8'=0L)

```  
### **Variable label**: Employment status   
**Variable name**: sdc_employ_1    
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in paid employment   
1 | Currently in paid employment  

**Harmonization status**:  complete    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_1$sdc_employ_1<-ifelse(!is.na(GLOBE1997$r56a),GLOBE1997$r56a,ifelse(!is.na(GLOBE1997$g20a),GLOBE1997$g20a,NA))

sdc_GLOBE_1$sdc_employ_1<-recode(as.integer(sdc_GLOBE_1$sdc_employ_1),'1'=1L,'2'=0L,'3'=0L,'4'=0L,'5'=0L,'6'=0L,'7'=0L)

```  
### **Variable label**: Employment status   
**Variable name**: sdc_employ_2    
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in paid employment   
1 | Currently in paid employment   

**Harmonization status**:  complete    
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_2$sdc_employ_2<-recode(as.integer(GLOBE2004$w243),'1'=1L,'2'=1L,'3'=0L,'4'=0L,'5'=0L,'6'=0L,'7'=0L,'8'=1L)

```  
### **Variable label**: Employment status   
**Variable name**: sdc_employ_3    
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in paid employment   
1 | Currently in paid employment   

**Harmonization status**:  complete    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_3$sdc_employ_3<-recode(as.integer(GLOBE2011$v7_werks),'1'=1L,'2'=1L,'3'=1L,'4'=0L,'5'=0L,'6'=0L,'7'=0L,'8'=0L)

```  
### **Variable label**: Employment status   
**Variable name**: sdc_employ_4    
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in paid employment   
1 | Currently in paid employment   

**Harmonization status**:  complete    
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_4$sdc_employ_4<-recode(as.integer(GLOBE2014$G14v12),'1'=1L,'2'=1L,'3'=1L,'4'=0L,'5'=0L,'6'=0L,'7'=0L,'8'=0L)

```  
### **Variable label**: Employment status   
**Variable name**: sdc_employ_5    
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in paid employment   
1 | Currently in paid employment   

**Harmonization status**:   impossible  
**Harmonization comment**:   
**R script**:   
```{r, echo=TRUE}


```  
### **Variable label**: Employment status   
**Variable name**: sdc_employ_6    
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in paid employment   
1 | Currently in paid employment   

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Retirement status   
**Variable name**: sdc_retire_0     
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in retirement   
1 | Currently in retirement   

**Harmonization status**:  complete    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_0$sdc_retire_0<-recode(as.integer(GLOBE1991$v247),'1'=0L,'2'=0L,'3'=0L,'4'=0L,'5'=1L,'6'=0L,'7'=0L,'8'=0L)

```  
### **Variable label**: Retirement status   
**Variable name**: sdc_retire_1     
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in retirement   
1 | Currently in retirement   

**Harmonization status**:  complete    
**Harmonization comment**:       
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_1$sdc_retire_1<-ifelse(!is.na(GLOBE1997$r56a),GLOBE1997$r56a,ifelse(!is.na(GLOBE1997$g20a),GLOBE1997$g20a,NA))

sdc_GLOBE_1$sdc_retire_1<-recode(as.integer(sdc_GLOBE_1$sdc_retire_1),'1'=0L,'2'=0L,'3'=0L,'4'=0L,'5'=1L,'6'=0L,'7'=0L)

```  
### **Variable label**: Retirement status   
**Variable name**: sdc_retire_2     
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in retirement   
1 | Currently in retirement   

**Harmonization status**:  complete    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_2$sdc_retire_2<-recode(as.integer(GLOBE2004$w243),'1'=0L,'2'=0L,'3'=0L,'4'=1L,'5'=0L,'6'=0L,'7'=0L,'8'=0L)

```  
### **Variable label**: Retirement status   
**Variable name**: sdc_retire_3     
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in retirement   
1 | Currently in retirement   

**Harmonization status**:  complete    
**Harmonization comment**:       
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_3$sdc_retire_3<-recode(as.integer(GLOBE2011$v7_werks),'1'=0L,'2'=0L,'3'=0L,'4'=0L,'5'=0L,'6'=0L,'7'=1L,'8'=0L)

```  
### **Variable label**: Retirement status   
**Variable name**: sdc_retire_4     
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in retirement   
1 | Currently in retirement   

**Harmonization status**:  complete    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_4$sdc_retire_4<-recode(as.integer(GLOBE2014$G14v12),'1'=0L,'2'=0L,'3'=0L,'4'=0L,'5'=1L,'6'=0L,'7'=0L,'8'=0L)

```  
### **Variable label**: Retirement status   
**Variable name**: sdc_retire_5     
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in retirement   
1 | Currently in retirement   

**Harmonization status**:  impossible  
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Retirement status   
**Variable name**: sdc_retire_6      
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in retirement   
1 | Currently in retirement   

**Harmonization status**:  impossible  
**Harmonization comment**:       
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Retirement age   
**Variable name**: sdc_retire_age_0      
**Variable description**: Age of the participant at retirement.  
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Retirement age    
**Variable name**: sdc_retire_age_1    
**Variable description**: Age of the participant at retirement.  
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Retirement age    
**Variable name**: sdc_retire_age_2    
**Variable description**: Age of the participant at retirement.    
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  

# Education and income subdomain

### **Variable label**: Highest level of education completed (ISCED 2011)    
**Variable name**: sdc_highest_edu_0       
**Variable description**: Highest level of education completed by the participant in accordance with the International Standard Classification of Education (ISCED 2011).       
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Lower secondary or less (ISCED 0-2)  
2 | Upper secondary (ISCED 3)
3 | Post-secondary non-tertiary education or short-cycle tertiary education (ISCED 4,5)
4 | Bachelor,master,doctoral or equivalent (ISCED 6,7,8)

**Harmonization status**:   complete    
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_0$sdc_highest_edu_0<-recode(as.factor(GLOBE1991$v244),"1"=1L,"2"=1L,"3"=1L,"4"=2L,"5"=2L,"6"=4L,"7"=4L,.default=NA_integer_) 

```  
### **Variable label**: Highest level of education completed (ISCED 2011)    
**Variable name**: sdc_highest_edu_1     
**Variable description**: Highest level of education completed by the participant in accordance with the International Standard Classification of Education (ISCED 2011).     
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Lower secondary or less (ISCED 0-2)  
2 | Upper secondary (ISCED 3)
3 | Post-secondary non-tertiary education or short-cycle tertiary education (ISCED 4,5)
4 | Bachelor,master,doctoral,or equivalent (ISCED 6,7,8)

**Harmonization status**:   impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```  
### **Variable label**: Highest level of education completed (ISCED 2011)    
**Variable name**: sdc_highest_edu_2     
**Variable description**: Highest level of education completed by the participant in accordance with the International Standard Classification of Education (ISCED 2011).     
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Lower secondary or less (ISCED 0-2)  
2 | Upper secondary (ISCED 3)
3 | Post-secondary non-tertiary education or short-cycle tertiary education (ISCED 4,5)
4 | Bachelor,master,doctoral,or equivalent (ISCED 6,7,8)

**Harmonization status**:  complete    
**Harmonization comment**:      
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_2$sdc_highest_edu_2<-recode(as.integer(GLOBE2004$w260),"1"=1L,"2"=1L,"3"=1L,"4"=1L,"5"=2L,"6"=2L,"7"=4L,"8"=4L,.default=NA_integer_)
```  
### **Variable label**: Highest level of education completed (ISCED 2011)    
**Variable name**: sdc_highest_edu_3     
**Variable description**: Highest level of education completed by the participant in accordance with the International Standard Classification of Education (ISCED 2011).     
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Lower secondary or less (ISCED 0-2)  
2 | Upper secondary (ISCED 3)
3 | Post-secondary non-tertiary education or short-cycle tertiary education (ISCED 4,5)
4 | Bachelor,master,doctoral,or equivalent (ISCED 6,7,8)

**Harmonization status**:  complete  
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_3$sdc_highest_edu_3<-recode(as.integer(GLOBE2011$v9_opleiding_opl_1),"1"=1L,"2"=1L,"3"=1L,"4"=1L,"5"=2L,"6"=2L,"7"=4L,"8"=4L,.default=NA_integer_)

```  
### **Variable label**: Highest level of education completed (ISCED 2011)    
**Variable name**: sdc_highest_edu_4     
**Variable description**: Highest level of education completed by the participant in accordance with the International Standard Classification of Education (ISCED 2011).     
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Lower secondary or less (ISCED 0-2)  
2 | Upper secondary (ISCED 3)
3 | Post-secondary non-tertiary education or short-cycle tertiary education (ISCED 4,5)
4 | Bachelor,master,doctoral,or equivalent (ISCED 6,7,8)

**Harmonization status**:  complete  
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_4$sdc_highest_edu_4<-recode(as.integer(GLOBE2014$G14v8_opl1),"1"=1L,"2"=1L,"3"=1L,"4"=1L,"5"=2L,"6"=2L,"7"=4L,"8"=4L,.default=NA_integer_)

```  
### **Variable label**: Post-secondary education    
**Variable name**: sdc_postsec_edu_0       
**Variable description**: Indicator of whether the participant completed highschool or post-secondary education.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Upper secondary or less (ISCED 0-3)
1 | Post-secondary non-tertiary education or more (ISCED 4-8)  

**Harmonization status**:  complete  
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_0$sdc_postsec_edu_0<-recode(as.factor(GLOBE1991$v244),"1"=0L,"2"=0L,"3"=0L,"4"=0L,"5"=0L,"6"=1L,"7"=1L,.default=NA_integer_) 


```  
### **Variable label**: Post-secondary education    
**Variable name**: sdc_postsec_edu_1     
**Variable description**: Indicator of whether the participant completed highschool or post-secondary education.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Upper secondary or less (ISCED 0-3)
1 | Post-secondary non-tertiary education or more (ISCED 4-8)    

**Harmonization status**:  impossible  
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Post-secondary education    
**Variable name**: sdc_postsec_edu_2     
**Variable description**: Indicator of whether the participant completed highschool or post-secondary education.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Upper secondary or less (ISCED 0-3)
1 | Post-secondary non-tertiary education or more (ISCED 4-8)    

**Harmonization status**:  complete  
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_2$sdc_postsec_edu_2<-recode(as.integer(GLOBE2004$w260),"1"=0L,"2"=0L,"3"=0L,"4"=0L,"5"=0L,"6"=0L,"7"=1L,"8"=1L,.default=NA_integer_)

```  
### **Variable label**: Post-secondary education    
**Variable name**: sdc_postsec_edu_3     
**Variable description**: Indicator of whether the participant completed highschool or post-secondary education.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Upper secondary or less (ISCED 0-3)
1 | Post-secondary non-tertiary education or more (ISCED 4-8)    

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_3$sdc_postsec_edu_3<-recode(as.integer(GLOBE2011$v9_opleiding_opl_1),"1"=0L,"2"=0L,"3"=0L,"4"=0L,"5"=0L,"6"=0L,"7"=1L,"8"=1L,.default=NA_integer_)

```  
### **Variable label**: Post-secondary education    
**Variable name**: sdc_postsec_edu_4     
**Variable description**: Indicator of whether the participant completed highschool or post-secondary education.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Upper secondary or less (ISCED 0-3)
1 | Post-secondary non-tertiary education or more (ISCED 4-8)    

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_4$sdc_postsec_edu_4<-recode(as.integer(GLOBE2014$G14v8_opl1),"1"=0L,"2"=0L,"3"=0L,"4"=0L,"5"=0L,"6"=0L,"7"=1L,"8"=1L,.default=NA_integer_)

```  
### **Variable label**: Net annual household income    
**Variable name**: sdc_income_0       
**Variable description**: Indicator of whether the net annual household income is above or below the country-specific net mean household income.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income    

**Harmonization status**:   complete  
**Harmonization comment**:   The question was asked to a subset of participants.Annual net household income taken from OECD. We took the value of the year 1990. (13916) A conversion rate from Dutch Guilder to EURO of 0.45 was used.  
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_0$sdc_income_0<-ifelse(!is.na(GLOBE1991$SEVMv812),GLOBE1991$SEVMv812,
                                 ifelse(!is.na(GLOBE1991$SEGVv639),GLOBE1991$SEGVv639,NA))
sdc_GLOBE_0$sdc_income_0<-ifelse(sdc_GLOBE_0$sdc_income_0==8|sdc_GLOBE_0$sdc_income_0==9|sdc_GLOBE_0$sdc_income_0==10|sdc_GLOBE_0$sdc_income_0==11|sdc_GLOBE_0$sdc_income_0==12|sdc_GLOBE_0$sdc_income_0==13,1L,ifelse(is.na(sdc_GLOBE_0$sdc_income_0) | sdc_GLOBE_0$sdc_income_0==99,NA,0L))
```  
### **Variable label**: Net annual household income    
**Variable name**: sdc_income_1       
**Variable description**: Indicator of whether the net annual household income is above or below the country-specific net mean household income.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income    

**Harmonization status**:  complete  
**Harmonization comment**:   Annual net household income taken from OECD. We took the value of the year 1995. (16143) A conversion rate from Dutch Guilder to EURO of 0.45 was used.  
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_1$sdc_income_1<-ifelse(!is.na(GLOBE1997$g26a),GLOBE1997$g26a,
                                 ifelse(!is.na(GLOBE1997$r62a),GLOBE1997$r62a,NA))
sdc_GLOBE_1$sdc_income_1<-ifelse(sdc_GLOBE_1$sdc_income_1=='P'|sdc_GLOBE_1$sdc_income_1=='Q'|sdc_GLOBE_1$sdc_income_1=='R'|sdc_GLOBE_1$sdc_income_1=='S'|sdc_GLOBE_1$sdc_income_1=='T'|sdc_GLOBE_1$sdc_income_1=='U',1L,ifelse(is.na(sdc_GLOBE_1$sdc_income_1) | sdc_GLOBE_1$sdc_income_1=='-2',NA,0L))

```    
### **Variable label**: Net annual household income    
**Variable name**: sdc_income_2       
**Variable description**: Indicator of whether the net annual household income is above or below the country-specific net mean household income.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income    

**Harmonization status**:  
**Harmonization comment**:   Net annual income for Netherland in 2004 is not available in OECD stats. So we took 2005 value (23895).     
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_2$sdc_income_2<-recode(as.integer(GLOBE2004$w277),'1'=0L,'2'=0L,'3'=0L,'4'=1L,.default=NA_integer_)

```   
### **Variable label**: Net annual household income    
**Variable name**: sdc_income_3       
**Variable description**: Indicator of whether the net annual household income is above or below the country-specific net mean household income.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income    

**Harmonization status**:  complete  
**Harmonization comment**:   Annual household income in 2011 for Netherland is 26000 according to OECD website.  
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_3$sdc_income_3<-recode(as.integer(GLOBE2011$v67_inkomen),'1'=0L,'2'=0L,'3'=0L,'4'=1L,'5'=1L,.default=NA_integer_)

```   
### **Variable label**: Net annual household income    
**Variable name**: sdc_income_4       
**Variable description**: Indicator of whether the net annual household income is above or below the country-specific net mean household income.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income    

**Harmonization status**:  complete  
**Harmonization comment**:   Annual household income in 2014 for Netherland is 29000 according to OECD website.  
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_4$sdc_income_4<-recode(as.integer(GLOBE2014$G14v93),'1'=0L,'2'=0L,'3'=0L,'4'=1L,'5'=1L,.default=NA_integer_)

```   
### **Variable label**: Net annual household income    
**Variable name**: sdc_income_5       
**Variable description**: Indicator of whether the net annual household income is above or below the country-specific net mean household income.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income    

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Net annual household income    
**Variable name**: sdc_income_6       
**Variable description**: Indicator of whether the net annual household income is above or below the country-specific net mean household income.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income    

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:   
```{r, echo=TRUE}


```  
# Marital status subdomain

### **Variable label**: Civil status    
**Variable name**: sdc_civstat_0      
**Variable description**: Indicator of the participant's current civil status.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently single or unmarried   
1 | Currently married or living with partner
2 | Currently divorced or separated
3 | Currently widowed  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:   
```{r, echo=TRUE}
sdc_GLOBE_0$sdc_civstat_0<-recode(as.integer(GLOBE1991$v279),'1'=1L,'2'=0L,'3'=2L,'4'=3L) 
```  
### **Variable label**: Civil status    
**Variable name**: sdc_civstat_1      
**Variable description**: Indicator of the participant's current civil status.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently single or unmarried   
1 | Currently married or living with partner
2 | Currently divorced or separated
3 | Currently widowed  

**Harmonization status**:  complete  
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_1$sdc_civstat_1<-ifelse(!is.na(GLOBE1997$g2a),GLOBE1997$g2a,
                                  ifelse(!is.na(GLOBE1997$r45a),GLOBE1997$r45a,NA))
sdc_GLOBE_1$sdc_civstat_1<-recode(sdc_GLOBE_1$sdc_civstat_1,'1'=1L,'2'=0L,'3'=2L,'4'=3L)
```   
### **Variable label**: Civil status     
**Variable name**: sdc_civstat_2      
**Variable description**: Indicator of the participant's current civil status.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently single or unmarried   
1 | Currently married or living with partner
2 | Currently divorced or separated
3 | Currently widowed  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_2$sdc_civstat_2<-recode(as.integer(GLOBE2004$w258),'1'=1L,'2'=1L,'3'=0L,'4'=2L,'5'=3L)

```   
### **Variable label**: Civil status    
**Variable name**: sdc_civstat_3        
**Variable description**: Indicator of the participant's current civil status.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently single or unmarried   
1 | Currently married or living with partner
2 | Currently divorced or separated
3 | Currently widowed  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:   
```{r, echo=TRUE}
sdc_GLOBE_3$sdc_civstat_3<-recode(as.integer(GLOBE2011$v5_burger_staat),'1'=1L,'2'=1L,'3'=0L,'4'=2L,'5'=3L)

```  
### **Variable label**: Civil status    
**Variable name**: sdc_civstat_4      
**Variable description**: Indicator of the participant's current civil status.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently single or unmarried   
1 | Currently married or living with partner
2 | Currently divorced or separated
3 | Currently widowed  

**Harmonization status**:  complete  
**Harmonization comment**:    
**R script**:   
```{r, echo=TRUE}
sdc_GLOBE_4$sdc_civstat_4<-recode(as.integer(GLOBE2014$G14v5),'1'=1L,'2'=0L,'3'=2L,'4'=3L)

```   
### **Variable label**: Civil status    
**Variable name**: sdc_civstat_5      
**Variable description**: Indicator of the participant's current civil status.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently single or unmarried   
1 | Currently married or living with partner
2 | Currently divorced or separated
3 | Currently widowed  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   
### **Variable label**: Civil status    
**Variable name**: sdc_civstat_6      
**Variable description**: Indicator of the participant's current civil status.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently single or unmarried   
1 | Currently married or living with partner
2 | Currently divorced or separated
3 | Currently widowed  

**Harmonization status**:  impossible    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```    
### **Variable label**: Married or living with partner  
**Variable name**: sdc_livstat_0      
**Variable description**: Indicator of whether the participant is currently married or is currently living with a spouse or a partner in a common household.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not married or living with partner   
1 | Currently married or living with partner  

**Harmonization status**:  complete  
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_0$sdc_livstat_0<-ifelse(GLOBE1991$v279=="1",1L,recode(as.integer(GLOBE1991$v307),'1'=1L,'2'=0L,'3'=0L,'4'=0L,'5'=0L,'6'=0L,'7'=0L))

```  
### **Variable label**: Married or living with partner  
**Variable name**: sdc_livstat_1      
**Variable description**: Indicator of whether the participant is currently married or is currently living with a spouse or a partner in a common household.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not married or living with partner   
1 | Currently married or living with partner  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_1$sdc_livstat_1<-ifelse(!is.na(GLOBE1997$g2b),GLOBE1997$g2b,
                                  ifelse(!is.na(GLOBE1997$r45b),GLOBE1997$r45b,NA))
sdc_GLOBE_1$sdc_livstat_1<-recode(sdc_GLOBE_1$sdc_livstat_1,'1'=1L,'2'=0L,'3'=0L,'4'=0L,'5'=0L)
```   
### **Variable label**: Married or living with partner  
**Variable name**: sdc_livstat_2      
**Variable description**: Indicator of whether the participant is currently married or is currently living with a spouse or a partner in a common household.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not married or living with partner   
1 | Currently married or living with partner  

**Harmonization status**:  complete  
**Harmonization comment**:       
**R script**:   
```{r, echo=TRUE}
sdc_GLOBE_2$sdc_livstat_2<-recode(as.integer(GLOBE2004$w259),'1'=1L,'2'=0L,'3'=0L,'4'=0L,'5'=0L)
```  
### **Variable label**: Married or living with partner  
**Variable name**: sdc_livstat_3      
**Variable description**: Indicator of whether the participant is currently married or is currently living with a spouse or a partner in a common household.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not married or living with partner   
1 | Currently married or living with partner  

**Harmonization status**:  complete   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_3$sdc_livstat_3<-recode(as.integer(GLOBE2011$v6_woons),'1'=1L,'2'=0L,'3'=0L,'4'=0L,'5'=0L)
```  
### **Variable label**: Married or living with partner  
**Variable name**: sdc_livstat_4      
**Variable description**: Indicator of whether the participant is currently married or is currently living with a spouse or a partner in a common household.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not married or living with partner   
1 | Currently married or living with partner  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_4$sdc_livstat_4<-recode(as.integer(GLOBE2014$G14v6),'1'=1L,'2'=0L)
```  
### **Variable label**: Married or living with partner  
**Variable name**: sdc_livstat_5      
**Variable description**: Indicator of whether the participant is currently married or is currently living with a spouse or a partner in a common household.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not married or living with partner   
1 | Currently married or living with partner  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```    
### **Variable label**: Married or living with partner  
**Variable name**: sdc_livstat_6      
**Variable description**: Indicator of whether the participant is currently married or is currently living with a spouse or a partner in a common household.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not married or living with partner   
1 | Currently married or living with partner  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```   


# Number of people in household subdomain

### **Variable label**: Number people in household  
**Variable name**: sdc_num_pplhh_0      
**Variable description**: Number of people currently living in the same household, including the participant.    
**Value type**: integer      
**Variable unit**: individuals  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   v157 represents the number of people in household, but equals to 8 when the value exceeds 8.  
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Number people in household  
**Variable name**: sdc_num_pplhh_1    
**Variable description**: Number of people currently living in the same household, including the participant.    
**Value type**: integer      
**Variable unit**: individuals  
**Category coding**: N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Number people in household  
**Variable name**: sdc_num_pplhh_2    
**Variable description**: Number of people currently living in the same household, including the participant.    
**Value type**: integer      
**Variable unit**: individuals  
**Category coding**: N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_2$sdc_num_pplhh_2<-GLOBE2004$w042

``` 
### **Variable label**: Number people in household  
**Variable name**: sdc_num_pplhh_3    
**Variable description**: Number of people currently living in the same household, including the participant.    
**Value type**: integer      
**Variable unit**: individuals  
**Category coding**: N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_3$sdc_num_pplhh_3<-GLOBE2011$v51_pers_won

``` 
### **Variable label**: Number people in household  
**Variable name**: sdc_num_pplhh_4    
**Variable description**: Number of people currently living in the same household, including the participant.    
**Value type**: integer      
**Variable unit**: individuals  
**Category coding**: N/A  

**Harmonization status**:  complete  
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_4$sdc_num_pplhh_4<-GLOBE2014$G14v89

``` 
### **Variable label**: Number children in household  
**Variable name**: sdc_num_childhh_0    
**Variable description**: Number of children (biological or adopted) currently living in the same household as the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Number children in household  
**Variable name**: sdc_num_childhh_1     
**Variable description**: Number of children (biological or adopted) currently living in the same household as the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Number children in household  
**Variable name**: sdc_num_childhh_2     
**Variable description**: Number of children (biological or adopted) currently living in the same household as the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Number children in household  
**Variable name**: sdc_num_childhh_3     
**Variable description**: Number of children (biological or adopted) currently living in the same household as the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Number of children in household   
**Variable name**: sdc_num_childhh_4  
**Variable description**: Number of children (biological or adopted) currently living in the same household as the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:  impossible    
**Harmonization comment**:     	In G14v10 we don't know if those children are participants' children.  
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Number of children 
**Variable name**: sdc_num_child_0  
**Variable description**: Number of children (biological or adopted) of the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   V335=8 when number of children is greater then 8.  
**R script**:  
```{r, echo=TRUE}


```    
### **Variable label**: Number of children  
**Variable name**: sdc_num_child_1  
**Variable description**: Number of children (biological or adopted) of the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:       
**R script**:  
```{r, echo=TRUE}


```   
### **Variable label**: Number of children  
**Variable name**: sdc_num_child_2  
**Variable description**: Number of children (biological or adopted) of the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```   
### **Variable label**: Number of children  
**Variable name**: sdc_num_child_3  
**Variable description**: Number of children (biological or adopted) of the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

```   
### **Variable label**: Number of children   
**Variable name**: sdc_num_child_4  
**Variable description**: Number of children (biological or adopted) of the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**:  complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_4$sdc_num_child_4<-GLOBE2014$G14v9

```    
### **Variable label**: Children (biological or adopted) 
**Variable name**: sdc_child_0  
**Variable description**: Indicator of wether the participant has any children (biological or adopted) or not.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Does not have children  
1 | Does have children

**Harmonization status**:  complete   
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_0$sdc_child_0<-as.integer(ifelse(GLOBE1991$v335>0,1,
                                ifelse(GLOBE1991$v335==0,0,NA)))

```    
### **Variable label**: Children (biological or adopted)  
**Variable name**: sdc_child_1   
**Variable description**: Indicator of wether the participant has any children (biological or adopted) or not.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Does not have children  
1 | Does have children

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Children (biological or adopted)  
**Variable name**: sdc_child_2   
**Variable description**: Indicator of wether the participant has any children (biological or adopted) or not.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Does not have children  
1 | Does have children

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Children (biological or adopted)  
**Variable name**: sdc_child_3   
**Variable description**: Indicator of wether the participant has any children (biological or adopted) or not.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Does not have children  
1 | Does have children

**Harmonization status**:  impossible  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}


```  
### **Variable label**: Children (biological or adopted)  
**Variable name**: sdc_child_4   
**Variable description**: Indicator of wether the participant has any children (biological or adopted) or not.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Does not have children  
1 | Does have children

**Harmonization status**:  complete 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_GLOBE_4$sdc_child_4<-as.integer(ifelse(GLOBE2014$G14v9==0,0,ifelse(GLOBE2014$G14v9>0,1,NA)))

```  