---
title: "Sociodemographic characteristics DataSchema"
output: html_document
---
```{r, echo=TRUE}
library(dplyr)
library(data.table)

# Connecting with Opal data server
## Login to server and assign study data
#Load Opal R library
library(opalr)
# Create an opal object with the login information
erasmus_opal <- opal.login()
#Login to Opal server and assign the content of the ROTTERDAM table(s) to your RStudio environment
opal.assign.table.tibble(erasmus_opal, 'RSII_MINDMAP_13082019_visit0','ROTTERDAM.RSII_MINDMAP_13082019_visit0', variables =NULL)

ROTTERDAM_0 <- opal.execute(erasmus_opal,'RSII_MINDMAP_13082019_visit0')


opal.assign.table.tibble(erasmus_opal, 'RSII_MINDMAP_13082019_visit1','ROTTERDAM.RSII_MINDMAP_13082019_visit1', variables =NULL)

ROTTERDAM_1 <- opal.execute(erasmus_opal,'RSII_MINDMAP_13082019_visit1')


opal.assign.table.tibble(erasmus_opal, 'RSII_MINDMAP_18102019_visit2','ROTTERDAM.RSII_MINDMAP_18102019_visit2', variables =NULL)

ROTTERDAM_2 <- opal.execute(erasmus_opal,'RSII_MINDMAP_18102019_visit2')

opal.assign.table.tibble(erasmus_opal, 'RSII_MINDMAP_18102019_visit3','ROTTERDAM.RSII_MINDMAP_18102019_visit3', variables =NULL)

ROTTERDAM_3 <- opal.execute(erasmus_opal,'RSII_MINDMAP_18102019_visit3')

opal.logout(erasmus_opal)


```
## Assign participant id as first column of your harmonized dataframes
```{r, echo=FALSE}

sdc_ROTTERDAM_0 <- data.frame(id = ROTTERDAM_0$id )
sdc_ROTTERDAM_1 <- data.frame(id = ROTTERDAM_1$id )
sdc_ROTTERDAM_2 <- data.frame(id = ROTTERDAM_2$id )
sdc_ROTTERDAM_3 <- data.frame(id = ROTTERDAM_3$id )

```
# Table of Contents
1. [Age and sex subdomain](#age-and-sex-subdomain) 
2. [Employment and retirement subdomain](#employment-and-retirement-subdomain)
3. [Education and income subdomain](#education-and-income-subdomain)
4. [Marital status subdomain](#marital-status-subdomain)
5. [Number of people in household subdomain](#number-of-people-in-household-subdomain)

# Age and sex subdomain

### **Variable label**: Age of participant   
**Variable name**: sdc_age_0      
**Variable description**: Age of the participant.      
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**: complete
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}
table(ROTTERDAM_0$ep_page, useNA="always")

## why ep_page (not startage)? One value different RS_MINDMAP__29406.
ROTTERDAM_0 %>% filter(ep_page!=startage) %>% select(id, ep_page, startage) 

sdc_ROTTERDAM_0<-as.integer(ROTTERDAM_0$ep_page)
```  
### **Variable label**: Age of participant   
**Variable name**: sdc_age_1       
**Variable description**: Age of the participant.      
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**: complete  
**Harmonization comment**:  Age at follow-up is calculated using the age starting to participate in the Rotterdam study, the age at starting the study and the date of Follow-up interview. 
**R script**:  
```{r, echo=TRUE}
MyMerge <- function(x,y){
  merge(x,y, by= c("id"),all=TRUE)
}
rot_table <- Reduce(MyMerge, list(ROTTERDAM_0,ROTTERDAM_1, ROTTERDAM_2, ROTTERDAM_3))

table(rot_table$startage.y, rot_table$ep_page)
table(ROTTERDAM_1$fup_visit_1, useNA="always")

## See above comment about one mismatch between startage and ep_page
sdc_ROTTERDAM_1$sdc_age_1<- as.integer(ROTTERDAM_1$startage)+ as.integer(substr(ROTTERDAM_1$fup_visit_1,1,4))- as.integer(substr(ROTTERDAM_1$startdat,1,4))
table(sdc_ROTTERDAM_1$sdc_age_1, useNA="always")

```  
### **Variable label**: Age of participant   
**Variable name**: sdc_age_2     
**Variable description**: Age of the participant.      
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**: complete  
**Harmonization comment**:  Age at follow-up is calculated using the age starting to participate in the Rotterdam study, the age at starting the study and the date of Follow-up interview.  
**R script**:  
```{r, echo=TRUE}
sdc_ROTTERDAM_2$sdc_age_2<- as.integer(ROTTERDAM_2$startage)+ as.integer(substr(ROTTERDAM_2$fup_visit_2,1,4))- as.integer(substr(ROTTERDAM_2$startdat,1,4))
table(sdc_ROTTERDAM_2$sdc_age_2, useNA="always")

```  
### **Variable label**: Age of participant   
**Variable name**: sdc_age_3     
**Variable description**: Age of the participant.     
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**: complete  
**Harmonization comment**:  Age at follow-up is calculated using the age starting to participate in the Rotterdam study, the age at starting the study and the date of Follow-up interview.   
**R script**:  
```{r, echo=TRUE}
sdc_ROTTERDAM_3$sdc_age_3<- as.integer(ROTTERDAM_3$startage)+ as.integer(substr(ROTTERDAM_3$fup_visit_3,1,4))- as.integer(substr(ROTTERDAM_3$startdat,1,4))
table(sdc_ROTTERDAM_3$sdc_age_3, useNA="always")

```  
### **Variable label**: Age of participant   
**Variable name**: sdc_age_4       
**Variable description**: Age of the participant.      
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Age of participant   
**Variable name**: sdc_age_5     
**Variable description**: Age of the participant.      
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Age of participant   
**Variable name**: sdc_age_6     
**Variable description**: Age of the participant.      
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Gender of participant   
**Variable name**: sdc_gender_0       
**Variable description**: Gender of the participant.      
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Male   
1 | Female   

**Harmonization status**: complete    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_ROTTERDAM_0$sdc_gender_0<-ROTTERDAM_0$sex

```  
### **Variable label**: Gender of participant   
**Variable name**: sdc_gender_1       
**Variable description**: Gender of the participant.      
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Male   
1 | Female   

**Harmonization status**: complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_ROTTERDAM_1$sdc_gender_1<-ROTTERDAM_1$sex

```  
### **Variable label**: Gender of participant   
**Variable name**: sdc_gender_2       
**Variable description**: Gender of the participant.      
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Male   
1 | Female   

**Harmonization status**: complete    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_ROTTERDAM_2$sdc_gender_2<-ROTTERDAM_2$sex

```  
### **Variable label**: Gender of participant   
**Variable name**: sdc_gender_3       
**Variable description**: Gender of the participant.      
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Male   
1 | Female   

**Harmonization status**: complete    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_ROTTERDAM_3$sdc_gender_3<-ROTTERDAM_3$sex

```  
### **Variable label**: Gender of participant   
**Variable name**: sdc_gender_4       
**Variable description**: Gender of the participant.      
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Male   
1 | Female   

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Gender of participant   
**Variable name**: sdc_gender_5       
**Variable description**: Gender of the participant.      
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Male   
1 | Female   

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Gender of participant   
**Variable name**: sdc_gender_6       
**Variable description**: Gender of the participant.      
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Male   
1 | Female   

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
# Employment and retirement subdomain

### **Variable label**: Employment status   
**Variable name**: sdc_employ_0       
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in paid employment   
1 | Currently in paid employment

**Harmonization status**: complete    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(ROTTERDAM_0$ep_ses2, useNA = "always")
sdc_ROTTERDAM_0$sdc_employ_0<-ifelse(ROTTERDAM_0$ep_ses2==0, 1L, ifelse(is.na(ROTTERDAM_0$ep_ses2), NA, 0L))
## 7 (I don't know) and 9 (No answer) also be 'NA'?

table(sdc_ROTTERDAM_0$sdc_employ_0, useNA="always")
```  
### **Variable label**: Employment status   
**Variable name**: sdc_employ_1    
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in paid employment   
1 | Currently in paid employment  

**Harmonization status**: complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

table(ROTTERDAM_1$e4_dises2, useNA = "always")
sdc_ROTTERDAM_1$sdc_employ_1<-ifelse(ROTTERDAM_1$e4_dises2==0, 1L, ifelse(is.na(ROTTERDAM_1$e4_dises2), NA, 0L))
## 7 (I don't know) and 9 (No answer) also be 'NA'?
table(sdc_ROTTERDAM_1$sdc_employ_1, useNA="always")

```  
### **Variable label**: Employment status   
**Variable name**: sdc_employ_2    
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in paid employment   
1 | Currently in paid employment   

**Harmonization status**: complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(ROTTERDAM_2$e5_EISES2, useNA = "always")
sdc_ROTTERDAM_2$sdc_employ_2<-ifelse(ROTTERDAM_2$e5_EISES2==0, 1L, ifelse(is.na(ROTTERDAM_2$e5_EISES2), NA, 0L))
## 7 (I don't know) and 9 (No answer) also be 'NA'?
table(sdc_ROTTERDAM_2$sdc_employ_2, useNA="always")
	
```  
### **Variable label**: Employment status   
**Variable name**: sdc_employ_3    
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in paid employment   
1 | Currently in paid employment   

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Employment status   
**Variable name**: sdc_employ_4    
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in paid employment   
1 | Currently in paid employment   

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Employment status   
**Variable name**: sdc_employ_5    
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in paid employment   
1 | Currently in paid employment   

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Employment status   
**Variable name**: sdc_employ_6    
**Variable description**: Indicator of whether the participant is currently in paid employment or is self-employed.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in paid employment   
1 | Currently in paid employment   

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Retirement status   
**Variable name**: sdc_retire_0     
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in retirement   
1 | Currently in retirement   

**Harmonization status**: complete    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

table(ROTTERDAM_0$ep_ses2, useNA = "always")
sdc_ROTTERDAM_0$sdc_retire_0<-ifelse(ROTTERDAM_0$ep_ses2==5|ROTTERDAM_0$ep_ses2==6, 1L, ifelse(is.na(ROTTERDAM_0$ep_ses2), NA, 0L))
## 7 (I don't know) and 9 (No answer) also be 'NA'?
table(sdc_ROTTERDAM_0$sdc_retire_0, useNA="always")

```  
### **Variable label**: Retirement status   
**Variable name**: sdc_retire_1     
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in retirement   
1 | Currently in retirement   

**Harmonization status**: complete   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(ROTTERDAM_1$e4_dises2, useNA = "always")
sdc_ROTTERDAM_1$sdc_retire_1<-ifelse(ROTTERDAM_1$e4_dises2==5|ROTTERDAM_1$e4_dises2==6, 1L, ifelse(is.na(ROTTERDAM_1$e4_dises2), NA, 0L))
## 7 (I don't know) and 9 (No answer) also be 'NA'?
table(sdc_ROTTERDAM_1$sdc_retire_1, useNA="always")


```  
### **Variable label**: Retirement status   
**Variable name**: sdc_retire_2     
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in retirement   
1 | Currently in retirement   

**Harmonization status**: complete   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
	
table(ROTTERDAM_2$e5_EISES2, useNA = "always")
sdc_ROTTERDAM_2$sdc_retire_2<-ifelse(ROTTERDAM_2$e5_EISES2==5|ROTTERDAM_2$e5_EISES2==5, 1L, ifelse(is.na(ROTTERDAM_2$e5_EISES2), NA, 0L))
## 7 (I don't know) and 9 (No answer) also be 'NA'?
table(sdc_ROTTERDAM_2$sdc_retire_2, useNA="always")

```  
### **Variable label**: Retirement status   
**Variable name**: sdc_retire_3     
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in retirement   
1 | Currently in retirement   

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Retirement status   
**Variable name**: sdc_retire_4     
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in retirement   
1 | Currently in retirement   

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Retirement status   
**Variable name**: sdc_retire_5     
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in retirement   
1 | Currently in retirement   

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Retirement status   
**Variable name**: sdc_retire_6      
**Variable description**: Indicator of whether the participant is currently retired.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not in retirement   
1 | Currently in retirement   

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Retirement age   
**Variable name**: sdc_retire_age_0      
**Variable description**: Age of the participant at retirement.  
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Retirement age    
**Variable name**: sdc_retire_age_1    
**Variable description**: Age of the participant at retirement.  
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Retirement age    
**Variable name**: sdc_retire_age_2    
**Variable description**: Age of the participant at retirement.    
**Value type**: integer    
**Variable unit**: years  
**Category coding**: N/A  

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  

# Education and income subdomain

### **Variable label**: Highest level of education completed (ISCED 2011)    
**Variable name**: sdc_highest_edu_0       
**Variable description**: Highest level of education completed by the participant in accordance with the International Standard Classification of Education (ISCED 2011).       
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Lower secondary or less (ISCED 0-2)  
2 | Upper secondary (ISCED 3)
3 | Post-secondary non-tertiary education or short-cycle tertiary education (ISCED 4,5)
4 | Bachelor,master,doctoral or equivalent (ISCED 6,7,8)

**Harmonization status**: complete   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(ROTTERDAM_0$ep_ses5)
table(ROTTERDAM_0$ep_ses5c)
table(ROTTERDAM_0$ep_ses5b, useNA="always")
table(ROTTERDAM_0$ep_ses5b,ROTTERDAM_0$ep_ses5c, useNA="always")

#people in each categories between the 2 variables are not the same. 

table(ROTTERDAM_0$ep_ses5, ROTTERDAM_0$ep_ses5c)
ROTTERDAM_0$ep_ses5c[ROTTERDAM_0$ep_ses5c>=88]<-NA
table(ROTTERDAM_0$ep_ses5c[ROTTERDAM_0$ep_ses5< ROTTERDAM_0$ep_ses5c])
table(ROTTERDAM_0$ep_ses5[ROTTERDAM_0$ep_ses5< ROTTERDAM_0$ep_ses5c])

table(ROTTERDAM_0$id[(ROTTERDAM_0$ep_ses5< ROTTERDAM_0$ep_ses5c)&ROTTERDAM_0$ep_ses5c<10])
#People with the IDs 28171, 34938 , 35858, 39781, 40926, 41884, 44347 have a higher value for the education they completed than of that they followed. 

# this creates a lot more NA values. Also
# sdc_ROTTERDAM_0$sdc_highest_edu_0<-ifelse((ROTTERDAM_0$ep_ses5b==1&(ROTTERDAM_0$ep_ses5==0|ROTTERDAM_0$ep_ses5==1|ROTTERDAM_0$ep_ses5==2))|
#                                             ROTTERDAM_0$ep_ses5c==0|ROTTERDAM_0$ep_ses5c==1|ROTTERDAM_0$ep_ses5c==2,1L,
#                                           ifelse((ROTTERDAM_0$ep_ses5b==1&(ROTTERDAM_0$ep_ses5==3|ROTTERDAM_0$ep_ses5==4))|
#                                             ROTTERDAM_0$ep_ses5c==3|ROTTERDAM_0$ep_ses5c==4,2L, 
#                                           ifelse((ROTTERDAM_0$ep_ses5b==1&(ROTTERDAM_0$ep_ses5==5))|
#                                             ROTTERDAM_0$ep_ses5c==5, 3L,
#                                           ifelse((ROTTERDAM_0$ep_ses5b==1&(ROTTERDAM_0$ep_ses5==6))|
#                                             ROTTERDAM_0$ep_ses5c==6, 4L, NA))))
# 
table(sdc_ROTTERDAM_0$sdc_highest_edu_0, useNA="always")

sdc_ROTTERDAM_0$sdc_highest_edu_0<-ifelse((ROTTERDAM_0$ep_ses5b==1&(ROTTERDAM_0$ep_ses5==0|ROTTERDAM_0$ep_ses5==1|ROTTERDAM_0$ep_ses5==2)),1L,
                                          ifelse((ROTTERDAM_0$ep_ses5b==1&(ROTTERDAM_0$ep_ses5==3|ROTTERDAM_0$ep_ses5==4)),2L,
                                          ifelse((ROTTERDAM_0$ep_ses5b==1&(ROTTERDAM_0$ep_ses5==5)), 3L,
                                          ifelse((ROTTERDAM_0$ep_ses5b==1&(ROTTERDAM_0$ep_ses5==6)), 4L, NA))))
#there is one participant for whom ep_sec5c gives information when the ep_sec5 and ep_sec5b doesn't (seen from cross tabulations above)
sdc_ROTTERDAM_0$sdc_highest_edu_0<-ifelse(ROTTERDAM_0$ep_ses5b==9& ROTTERDAM_0$ep_ses5c==0,1L, sdc_ROTTERDAM_0$sdc_highest_edu_0)
table(sdc_ROTTERDAM_0$sdc_highest_edu_0, useNA="always")

```  
### **Variable label**: Highest level of education completed (ISCED 2011)    
**Variable name**: sdc_highest_edu_1     
**Variable description**: Highest level of education completed by the participant in accordance with the International Standard Classification of Education (ISCED 2011).     
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Lower secondary or less (ISCED 0-2)  
2 | Upper secondary (ISCED 3)
3 | Post-secondary non-tertiary education or short-cycle tertiary education (ISCED 4,5)
4 | Bachelor,master,doctoral,or equivalent (ISCED 6,7,8)

**Harmonization status**: impossible 
**Harmonization comment**:   Study-specific category includes higher vocational education and university together.  
**R script**:  
```{r, echo=TRUE}
# table(ROTTERDAM_1$ses_UNESCO_recoded)
# 
# 0
# en primary education
# 1
# en lower/intermediate general education OR lower vocational education
# 2
# en intermediate vocational education OR higher general education
# 3
# en higher vocational education OR university
# 99
# en missing
```  
### **Variable label**: Highest level of education completed (ISCED 2011)    
**Variable name**: sdc_highest_edu_2     
**Variable description**: Highest level of education completed by the participant in accordance with the International Standard Classification of Education (ISCED 2011).     
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Lower secondary or less (ISCED 0-2)  
2 | Upper secondary (ISCED 3)
3 | Post-secondary non-tertiary education or short-cycle tertiary education (ISCED 4,5)
4 | Bachelor,master,doctoral,or equivalent (ISCED 6,7,8)

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Highest level of education completed (ISCED 2011)    
**Variable name**: sdc_highest_edu_3     
**Variable description**: Highest level of education completed by the participant in accordance with the International Standard Classification of Education (ISCED 2011).     
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Lower secondary or less (ISCED 0-2)  
2 | Upper secondary (ISCED 3)
3 | Post-secondary non-tertiary education or short-cycle tertiary education (ISCED 4,5)
4 | Bachelor,master,doctoral,or equivalent (ISCED 6,7,8)

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Highest level of education completed (ISCED 2011)    
**Variable name**: sdc_highest_edu_4     
**Variable description**: Highest level of education completed by the participant in accordance with the International Standard Classification of Education (ISCED 2011).     
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
1 | Lower secondary or less (ISCED 0-2)  
2 | Upper secondary (ISCED 3)
3 | Post-secondary non-tertiary education or short-cycle tertiary education (ISCED 4,5)
4 | Bachelor,master,doctoral,or equivalent (ISCED 6,7,8)

**Harmonization status**: impossible   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Post-secondary education    
**Variable name**: sdc_postsec_edu_0       
**Variable description**: Indicator of whether the participant completed high school or post-secondary education.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Upper secondary or less (ISCED 0-3)
1 | Post-secondary non-tertiary education or more (ISCED 4-8)  

**Harmonization status**: complete   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

sdc_ROTTERDAM_0$sdc_postsec_edu_0<-ifelse(sdc_ROTTERDAM_0$sdc_highest_edu_0==1|sdc_ROTTERDAM_0$sdc_highest_edu_0==2,0L, 
                                   ifelse(sdc_ROTTERDAM_0$sdc_highest_edu_0==3|sdc_ROTTERDAM_0$sdc_highest_edu_0==4,1L,NA))

table(sdc_ROTTERDAM_0$sdc_postsec_edu_0)
```  
### **Variable label**: Post-secondary education    
**Variable name**: sdc_postsec_edu_1     
**Variable description**: Indicator of whether the participant completed high school or post-secondary education.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Upper secondary or less (ISCED 0-3)
1 | Post-secondary non-tertiary education or more (ISCED 4-8)    

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#ses_UNESCO_recoded

```  
### **Variable label**: Post-secondary education    
**Variable name**: sdc_postsec_edu_2     
**Variable description**: Indicator of whether the participant completed high school or post-secondary education.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Upper secondary or less (ISCED 0-3)
1 | Post-secondary non-tertiary education or more (ISCED 4-8)    

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Post-secondary education    
**Variable name**: sdc_postsec_edu_3     
**Variable description**: Indicator of whether the participant completed high school or post-secondary education.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Upper secondary or less (ISCED 0-3)
1 | Post-secondary non-tertiary education or more (ISCED 4-8)    

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Post-secondary education    
**Variable name**: sdc_postsec_edu_4     
**Variable description**: Indicator of whether the participant completed high school or post-secondary education.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Upper secondary or less (ISCED 0-3)
1 | Post-secondary non-tertiary education or more (ISCED 4-8)    

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Net annual household income    
**Variable name**: sdc_income_0       
**Variable description**: Indicator of whether the net annual household income is above or below the country-specific net mean household income.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income    

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#ep_ses8
#monthly, categorical. Also secondarily couldn't find OECD stats for netherlands for 2001
```  
### **Variable label**: Net annual household income    
**Variable name**: sdc_income_1       
**Variable description**: Indicator of whether the net annual household income is above or below the country-specific net mean household income.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income    

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```    
### **Variable label**: Net annual household income    
**Variable name**: sdc_income_2       
**Variable description**: Indicator of whether the net annual household income is above or below the country-specific net mean household income.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income    

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```   
### **Variable label**: Net annual household income    
**Variable name**: sdc_income_3       
**Variable description**: Indicator of whether the net annual household income is above or below the country-specific net mean household income.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income    

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```   
### **Variable label**: Net annual household income    
**Variable name**: sdc_income_4       
**Variable description**: Indicator of whether the net annual household income is above or below the country-specific net mean household income.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income    

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```   
### **Variable label**: Net annual household income    
**Variable name**: sdc_income_5       
**Variable description**: Indicator of whether the net annual household income is above or below the country-specific net mean household income.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income    

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Net annual household income    
**Variable name**: sdc_income_6       
**Variable description**: Indicator of whether the net annual household income is above or below the country-specific net mean household income.    
**Value type**: integer  
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income    

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
# Marital status subdomain

### **Variable label**: Civil status    
**Variable name**: sdc_civstat_0      
**Variable description**: Indicator of the participant's current civil status.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently single or unmarried   
1 | Currently married or living with partner
2 | Currently divorced or separated
3 | Currently widowed  

**Harmonization status**: complete   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(ROTTERDAM_0$ep_ses1)	

sdc_ROTTERDAM_0$sdc_civstat_0<-ifelse(ROTTERDAM_0$ep_ses1==1, 0L,
                               ifelse(ROTTERDAM_0$ep_ses1==2|ROTTERDAM_0$ep_ses1==3|ROTTERDAM_0$ep_ses1==4|
                                      ROTTERDAM_0$ep_ses1==5|ROTTERDAM_0$ep_ses1==6|ROTTERDAM_0$ep_ses1==7,1L, 
                               ifelse(ROTTERDAM_0$ep_ses1==9,2L, ifelse(ROTTERDAM_0$ep_ses1==8, 3L,NA))))
## Disagree with assignment of source category 7 to harmonized category 1 (should be 2?)
## Also, should adjust for conflicts with ep_pid6 (living status)?
table(sdc_ROTTERDAM_0$sdc_civstat_0)

```  
### **Variable label**: Civil status    
**Variable name**: sdc_civstat_1      
**Variable description**: Indicator of the participant's current civil status.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently single or unmarried   
1 | Currently married or living with partner
2 | Currently divorced or separated
3 | Currently widowed  

**Harmonization status**: complete   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(ROTTERDAM_1$e4_dicivil)

sdc_ROTTERDAM_1$sdc_civstat_1<-ifelse(ROTTERDAM_1$e4_dicivil==1, 0L, 
                               ifelse(ROTTERDAM_1$e4_dicivil==2, 1L, ifelse(ROTTERDAM_1$e4_dicivil==4, 2L, 
                               ifelse(ROTTERDAM_1$e4_dicivil==3, 3L, NA))))

table(sdc_ROTTERDAM_1$sdc_civstat_1)


```   
### **Variable label**: Civil status    
**Variable name**: sdc_civstat_2      
**Variable description**: Indicator of the participant's current civil status.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently single or unmarried   
1 | Currently married or living with partner
2 | Currently divorced or separated
3 | Currently widowed  

**Harmonization status**: complete   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
sdc_ROTTERDAM_2$sdc_civstat_2<-ifelse(ROTTERDAM_2$e5_EICIVIL==1, 0L, 
                               ifelse(ROTTERDAM_2$e5_EICIVIL==2|ROTTERDAM_2$e5_EICIVIL==5, 1L, 
                               ifelse(ROTTERDAM_2$e5_EICIVIL==4, 2L, 
                               ifelse(ROTTERDAM_2$e5_EICIVIL==3, 3L, NA))))
table(sdc_ROTTERDAM_2$sdc_civstat_2)

```   
### **Variable label**: Civil status    
**Variable name**: sdc_civstat_3        
**Variable description**: Indicator of the participant's current civil status.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently single or unmarried   
1 | Currently married or living with partner
2 | Currently divorced or separated
3 | Currently widowed  

**Harmonization status**: complete   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

sdc_ROTTERDAM_3$sdc_civstat_3<- ifelse(ROTTERDAM_3$e6_EICIVIL==1, 0L, 
                                ifelse(ROTTERDAM_3$e6_EICIVIL==2, 1L, 
                                ifelse(ROTTERDAM_3$e6_EICIVIL==4, 2L, 
                                ifelse(ROTTERDAM_3$e6_EICIVIL==3, 3L, NA))))
table(sdc_ROTTERDAM_3$sdc_civstat_3)

```  
### **Variable label**: Civil status    
**Variable name**: sdc_civstat_4      
**Variable description**: Indicator of the participant's current civil status.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently single or unmarried   
1 | Currently married or living with partner
2 | Currently divorced or separated
3 | Currently widowed  

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```   
### **Variable label**: Civil status    
**Variable name**: sdc_civstat_5      
**Variable description**: Indicator of the participant's current civil status.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently single or unmarried   
1 | Currently married or living with partner
2 | Currently divorced or separated
3 | Currently widowed  

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```   
### **Variable label**: Civil status    
**Variable name**: sdc_civstat_6      
**Variable description**: Indicator of the participant's current civil status.    
**Value type**: integer    
**Variable unit**: N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently single or unmarried   
1 | Currently married or living with partner
2 | Currently divorced or separated
3 | Currently widowed  

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```    
### **Variable label**: Married or living with partner  
**Variable name**: sdc_livstat_0      
**Variable description**: Indicator of whether the participant is currently married or is currently living with a spouse or a partner in a common household.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not married or living with partner   
1 | Currently married or living with partner  

**Harmonization status**: complete  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
with(ROTTERDAM_0, table(ep_pid6, useNA = 'always'))
with(ROTTERDAM_0, table(ep_pid6, ep_ses1, useNA = 'always'))

sdc_ROTTERDAM_0$sdc_livstat_0<-ifelse(ROTTERDAM_0$ep_ses1==2|ROTTERDAM_0$ep_ses1==3|ROTTERDAM_0$ep_ses1==4|
                                      ROTTERDAM_0$ep_ses1==5|ROTTERDAM_0$ep_ses1==6|ROTTERDAM_0$ep_ses1==7,1L,
                              ifelse(ROTTERDAM_0$ep_ses1==8|ROTTERDAM_0$ep_ses1==1|ROTTERDAM_0$ep_ses1==9, 0L,NA))
## Disagree with assignment of source category 7 to harmonized category 1 (should be 2?)
## Also, should adjust for conflicts with ep_pid6 (living status)?
table(sdc_ROTTERDAM_0$sdc_civstat_0)
table(sdc_ROTTERDAM_0$sdc_livstat_0)

```  
### **Variable label**: Married or living with partner  
**Variable name**: sdc_livstat_1      
**Variable description**: Indicator of whether the participant is currently married or is currently living with a spouse or a partner in a common household.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not married or living with partner   
1 | Currently married or living with partner  

**Harmonization status**: complete    
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(ROTTERDAM_1$e4_dicivil)
with(ROTTERDAM_1, table(e4_dipar, useNA = 'always'))
with(ROTTERDAM_1, table(e4_dipar, e4_dicivil, useNA = 'always'))

sdc_ROTTERDAM_1$sdc_livstat_1<-ifelse(ROTTERDAM_1$e4_dicivil==1|ROTTERDAM_1$e4_dicivil==3|
                                      ROTTERDAM_1$e4_dicivil==4, 0L, 
                                ifelse(ROTTERDAM_1$e4_dicivil==2, 1L, NA))

table(sdc_ROTTERDAM_1$sdc_livstat_1)
table(sdc_ROTTERDAM_1$sdc_civstat_1)

```   
### **Variable label**: Married or living with partner  
**Variable name**: sdc_livstat_2      
**Variable description**: Indicator of whether the participant is currently married or is currently living with a spouse or a partner in a common household.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not married or living with partner   
1 | Currently married or living with partner  

**Harmonization status**: complete   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
with(ROTTERDAM_2, table(e5_EIPAR, useNA = 'always'))
with(ROTTERDAM_2, table(e5_EIPAR, e5_EICIVIL, useNA = 'always'))

sdc_ROTTERDAM_2$sdc_livstat_2<-ifelse(ROTTERDAM_2$e5_EICIVIL==2|ROTTERDAM_2$e5_EICIVIL==5, 1L,
                               ifelse(ROTTERDAM_2$e5_EICIVIL==4|ROTTERDAM_2$e5_EICIVIL==1|
                                      ROTTERDAM_2$e5_EICIVIL==3, 0L, NA))
table(sdc_ROTTERDAM_2$sdc_livstat_2)

```  
### **Variable label**: Married or living with partner  
**Variable name**: sdc_livstat_3      
**Variable description**: Indicator of whether the participant is currently married or is currently living with a spouse or a partner in a common household.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not married or living with partner   
1 | Currently married or living with partner  

**Harmonization status**: complete   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
with(ROTTERDAM_3, table(e6_EIPAR, useNA = 'always'))
with(ROTTERDAM_3, table(e6_EIPAR, e6_EICIVIL, useNA = 'always'))

sdc_ROTTERDAM_3$sdc_livstat_3<-ifelse(ROTTERDAM_3$e6_EICIVIL==2, 1L,
                               ifelse(ROTTERDAM_3$e6_EICIVIL==4|ROTTERDAM_3$e6_EICIVIL==1|ROTTERDAM_3$e6_EICIVIL==3, 0L, NA))
table(sdc_ROTTERDAM_3$sdc_livstat_3)
table(sdc_ROTTERDAM_3$sdc_civstat_3)

```  
### **Variable label**: Married or living with partner  
**Variable name**: sdc_livstat_4      
**Variable description**: Indicator of whether the participant is currently married or is currently living with a spouse or a partner in a common household.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not married or living with partner   
1 | Currently married or living with partner  

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Married or living with partner  
**Variable name**: sdc_livstat_5      
**Variable description**: Indicator of whether the participant is currently married or is currently living with a spouse or a partner in a common household.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not married or living with partner   
1 | Currently married or living with partner  

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```    
### **Variable label**: Married or living with partner  
**Variable name**: sdc_livstat_6      
**Variable description**: Indicator of whether the participant is currently married or is currently living with a spouse or a partner in a common household.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Currently not married or living with partner   
1 | Currently married or living with partner  

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```   


# Number of people in household subdomain

### **Variable label**: Number of people in household  
**Variable name**: sdc_num_pplhh_0      
**Variable description**: Number of people currently living in the same household, including the participant.    
**Value type**: integer      
**Variable unit**: individuals  
**Category coding**: N/A  

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Number of people in household  
**Variable name**: sdc_num_pplhh_1    
**Variable description**: Number of people currently living in the same household, including the participant.    
**Value type**: integer      
**Variable unit**: individuals  
**Category coding**: N/A  

**Harmonization status**: complete   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(ROTTERDAM_1$e4_dihomeap)
sdc_ROTTERDAM_1$sdc_num_pplhh_1<-ifelse(ROTTERDAM_1$e4_dihomeap==99, NA,ROTTERDAM_1$e4_dihomeap )
table(sdc_ROTTERDAM_1$sdc_num_pplhh_1)
```  
### **Variable label**: Number of people in household  
**Variable name**: sdc_num_pplhh_2    
**Variable description**: Number of people currently living in the same household, including the participant.    
**Value type**: integer      
**Variable unit**: individuals  
**Category coding**: N/A  

**Harmonization status**: complete   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}

table(ROTTERDAM_2$e5_EIHOMEAP)
sdc_ROTTERDAM_2$sdc_num_pplhh_2<-ifelse(ROTTERDAM_2$e5_EIHOMEAP==77, NA,ROTTERDAM_2$e5_EIHOMEAP)
table(sdc_ROTTERDAM_2$sdc_num_pplhh_2)

``` 
### **Variable label**: Number of people in household  
**Variable name**: sdc_num_pplhh_3    
**Variable description**: Number of people currently living in the same household, including the participant.    
**Value type**: integer      
**Variable unit**: individuals  
**Category coding**: N/A  

**Harmonization status**: complete   
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
table(ROTTERDAM_3$e6_EIHOMEAP)
sdc_ROTTERDAM_3$sdc_num_pplhh_3<-ifelse(ROTTERDAM_3$e6_EIHOMEAP==77, NA,ROTTERDAM_3$e6_EIHOMEAP)
table(sdc_ROTTERDAM_3$sdc_num_pplhh_3)

``` 
### **Variable label**: Number of people in household  
**Variable name**: sdc_num_pplhh_4    
**Variable description**: Number of people currently living in the same household, including the participant.    
**Value type**: integer      
**Variable unit**: individuals  
**Category coding**: N/A  

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

``` 
### **Variable label**: Number of children in household  
**Variable name**: sdc_num_childhh_0    
**Variable description**: Number of children (biological or adopted) currently living in the same household as the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Number of children in household  
**Variable name**: sdc_num_childhh_1     
**Variable description**: Number of children (biological or adopted) currently living in the same household as the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Number of children in household  
**Variable name**: sdc_num_childhh_2     
**Variable description**: Number of children (biological or adopted) currently living in the same household as the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Number of children in household  
**Variable name**: sdc_num_childhh_3     
**Variable description**: Number of children (biological or adopted) currently living in the same household as the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Number of children in household  
**Variable name**: sdc_num_childhh_4  
**Variable description**: Number of children (biological or adopted) currently living in the same household as the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Number of children 
**Variable name**: sdc_num_child_0  
**Variable description**: Number of children (biological or adopted) of the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```    
### **Variable label**: Number of children  
**Variable name**: sdc_num_child_1  
**Variable description**: Number of children (biological or adopted) of the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```   
### **Variable label**: Number of children  
**Variable name**: sdc_num_child_2  
**Variable description**: Number of children (biological or adopted) of the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```   
### **Variable label**: Number of children  
**Variable name**: sdc_num_child_3  
**Variable description**: Number of children (biological or adopted) of the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```   
### **Variable label**: Number of children   
**Variable name**: sdc_num_child_4  
**Variable description**: Number of children (biological or adopted) of the participant.    
**Value type**: integer      
**Variable unit**: children  
**Category coding**: N/A  

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```    
### **Variable label**: Children (biological or adopted) 
**Variable name**: sdc_child_0  
**Variable description**: Indicator of whether the participant has any children (biological or adopted) or not.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Does not have children  
1 | Does have children

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```    
### **Variable label**: Children (biological or adopted)  
**Variable name**: sdc_child_1   
**Variable description**: Indicator of whether the participant has any children (biological or adopted) or not.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Does not have children  
1 | Does have children

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Children (biological or adopted)  
**Variable name**: sdc_child_2   
**Variable description**: Indicator of whether the participant has any children (biological or adopted) or not.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Does not have children  
1 | Does have children

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Children (biological or adopted)  
**Variable name**: sdc_child_3   
**Variable description**: Indicator of whether the participant has any children (biological or adopted) or not.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Does not have children  
1 | Does have children

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  
### **Variable label**: Children (biological or adopted)  
**Variable name**: sdc_child_4   
**Variable description**: Indicator of whether the participant has any children (biological or adopted) or not.    
**Value type**: integer    
**Variable unit**: N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Does not have children  
1 | Does have children

**Harmonization status**: impossible 
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
 

```  