```{r, echo=TRUE}
library(epiDisplay)
library(tidyverse)
library(data.table)
```
# Age and sex subdomain

### **Variable label**: Age of participant   
**Variable name**: sdc_age_0      
**Validation script**:  
```{r, echo=TRUE}
identical(sdc_HUNT_0$sdc_age_0,HUNT1$PartAg_NT1BLQ1)
```
**Validation comment**: 

### **Variable label**: Age of participant   
**Variable name**: sdc_age_1      
**Validation script**:  
```{r, echo=TRUE}
identical(sdc_HUNT_1$sdc_age_1,HUNT2$PartAg_NT2BLQ1)
```  
**Validation comment**:  

### **Variable label**: Age of participant   
**Variable name**: sdc_age_2      
**Validation script**:
```{r, echo=TRUE}
identical(sdc_HUNT_2$sdc_age_2,HUNT3$PartAg_NT3BLQ1)
```  

### **Variable label**: Age of participant   
**Variable name**: sdc_gender_0      
**Validation script**:  
```{r, echo=TRUE}
summ(as.factor(sdc_HUNT_0$sdc_gender_0))

```  
**Validation comment**: 

### **Variable label**: Age of participant   
**Variable name**: sdc_gender_1      
**Validation script**:  
```{r, echo=TRUE}

```  
**Validation comment**: 

### **Variable label**: Age of participant   
**Variable name**: sdc_gender_2      
**Validation script**:  
```{r, echo=TRUE}

```  
**Validation comment**: 

### **Variable label**: Age of participant   
**Variable name**: sdc_gender_2      
**Validation script**:  
```{r, echo=TRUE}

```  
**Validation comment**: 

### **Variable label**: Employment status   
**Variable name**: sdc_employ_0  
**Validation script**:
```{r, echo=TRUE}
AfterH<-table(sdc_HUNT_0$sdc_employ_0,useNA = "always")
X<-table(HUNT1$`WorCu_NT1BLQ1`)
BeforeH<-c(sum(X["4"]),sum(X[c("1","2","3")]),sum(is.na(HUNT1$`WorCu_NT1BLQ1`)))
C <- rbind(BeforeH,AfterH)
colnames(C)<-c("0","1","NA")
```  
**Validation comment**:  

### **Variable label**: Employment status   
**Variable name**: sdc_employ_2  
**Validation script**:
```{r, echo=TRUE}
identical(sdc_HUNT_2$sdc_employ_2,HUNT3$WorCu_NT3BLI)
```  
**Validation comment**:  

### **Variable label**: Highest level of education completed (ISCED 2011) 
**Variable name**: sdc_highest_edu_0    
**Validation script**:
```{r, echo=TRUE}
AfterH<-table(sdc_HUNT_0$sdc_highest_edu_0,useNA = "always")
X<-table(HUNT1$Educ_NT1BLQ2,useNA = "always")
BeforeH<-c(sum(X[c("1","2","3","4")]),X["5"],X["6"],sum(X[c("7","8")]),sum(is.na(HUNT1$Educ_NT1BLQ2)))
C <- rbind(BeforeH,AfterH)
colnames(C)<-c("1","2","3","4","NA")
C
```  
**Validation comment**: General Certificate of Education, commercial college or sixth form college a ete recodee en 
upper secondary(ISCED 3).

### **Variable label**: Highest level of education completed (ISCED 2011)    
**Variable name**: sdc_highest_edu_1  
**R script**:  
```{r, echo=TRUE}
AfterH<-table(sdc_HUNT_1$sdc_highest_edu_1,useNA = "always")
X<-table(HUNT2$Educ_NT2BLQ1)
BeforeH<-c(X["1"],X["2"],X["3"],sum(X[c("4","5")]),sum(is.na(HUNT2$Educ_NT2BLQ1)))
C <- rbind(BeforeH,AfterH)
colnames(C)<-c("1","2","3","4","NA")
C
```
**Validation comment**:  Category 4 recode to upper secondary.

### **Variable label**: Post-secondary education    
**Variable name**: sdc_postsec_edu_0       
**R script**:  
```{r, echo=TRUE}
AfterH<-table(sdc_HUNT_0$sdc_postsec_edu_0,useNA = "always")
X<-table(HUNT1$Educ_NT1BLQ2,useNA = "always")
BeforeH<-c(sum(X[c("1","2","3","4")]),sum(X[c("5","6","7","8")]),sum(is.na(HUNT1$Educ_NT1BLQ2)))
C <- rbind(BeforeH,AfterH)
colnames(C)<-c("0","1","NA")
C
```
**Validation comment**:  

### **Variable label**: Post-secondary education    
**Variable name**: sdc_postsec_edu_1     
**R script**:  
```{r, echo=TRUE}
AfterH<-table(sdc_HUNT_1$sdc_postsec_edu_1,useNA = "always")
X<-table(HUNT2$Educ_NT2BLQ1)
BeforeH<-c(sum(X[c("1","2","3")]),sum(X[c("4","5")]),sum(is.na(HUNT2$Educ_NT2BLQ1)))
C <- rbind(BeforeH,AfterH)
colnames(C)<-c("0","1","NA")
C
```
**Validation comment**:

### **Variable label**: Civil status    
**Variable name**: sdc_civstat_0    
**R script**:  
```{r, echo=TRUE}
AfterH<-table(sdc_HUNT_0$sdc_civstat_0,useNA = "always")
X<-table(HUNT1$MaritStat_NT1BLQ1,useNA = "always")
BeforeH<-c(X["1"],X["2"],sum(X[c("4","5")]),X["3"],sum(is.na(HUNT1$MaritStat_NT1BLQ1)))
C <- rbind(BeforeH,AfterH)
colnames(C)<-c("0","1","2","3","NA")
C
```
**Validation comment**:  

### **Variable label**: Civil status    
**Variable name**: sdc_civstat_1    
**R script**:  
```{r, echo=TRUE}
AfterH<-table(sdc_HUNT_1$sdc_civstat_1,useNA = "always")
X<-table(HUNT2$MaritStat_NT2BLQ2,useNA = "always")
BeforeH<-c(X["1"],sum(X[c("2","6")],na.rm=TRUE),sum(X[c("4","5","7","8")],na.rm = TRUE),sum(X[c("3","9")],na.rm = TRUE),sum(is.na(HUNT2$MaritStat_NT2BLQ2)))
C <- rbind(BeforeH,AfterH)
colnames(C)<-c("0","1","2","3","NA")
C
```
**Validation comment**:  

### **Variable label**: Civil status    
**Variable name**: sdc_civstat_2  
**R script**:  
```{r, echo=TRUE}
AfterH<-table(sdc_HUNT_2$sdc_civstat_2,useNA = "always")
X<-table(HUNT3$MaritStat_NT3BLQ1)
BeforeH<-c(X["1"],sum(X[c("2","6")]),sum(X[c("4","5","7","8")],na.rm = TRUE),sum(X[c("3","9")]),sum(is.na(HUNT3$MaritStat_NT3BLQ1)))
C <- rbind(BeforeH,AfterH)
colnames(C)<-c("0","1","2","3","NA")
C
```
**Validation comment**:  

### **Variable label**: Married or living with partner  
**Variable name**: sdc_livstat_0      
**R script**:  
```{r, echo=TRUE}
AfterH<-table(sdc_HUNT_0$sdc_livstat_0,useNA = "always")
X<-table(HUNT1$MaritStat_NT1BLQ1)
BeforeH<-c(sum(X[c("1","3","4","5")]),X["2"],sum(is.na(HUNT1$MaritStat_NT1BLQ1)))
C <- rbind(BeforeH,AfterH)
colnames(C)<-c("0","1","NA")
C
```
**Validation comment**:  

### **Variable label**: Married or living with partner  
**Variable name**: sdc_livstat_1      
**R script**:  
```{r, echo=TRUE}
AfterH<-table(sdc_HUNT_1$sdc_livstat_1,useNA = "always")
X<-table(HUNT2$MaritStat_NT2BLQ2,useNA = "always")
BeforeH<-c(sum(X[c("1","3","4","5","7","8","9")],na.rm = TRUE),sum(X[c("2","6")],na.rm = TRUE),sum(is.na(HUNT2$MaritStat_NT2BLQ2)))
C <- rbind(BeforeH,AfterH)
colnames(C)<-c("0","1","NA")
C
```
**Validation comment**:  

### **Variable label**: Married or living with partner  
**Variable name**: sdc_livstat_2      
**R script**:  
```{r, echo=TRUE}
AfterH<-table(sdc_HUNT_2$sdc_livstat_2,useNA = "always")
X<-table(HUNT3$MaritStat_NT3BLQ1)
BeforeH<-c(sum(X[c("1","3","4","5","7","8","9")],na.rm = TRUE),sum(X[c("2","6")],na.rm = TRUE),sum(is.na(HUNT3$MaritStat_NT3BLQ1)))
C <- rbind(BeforeH,AfterH)
colnames(C)<-c("0","1","NA")
C
```

### **Variable label**: Number people in household  
**Variable name**: sdc_num_pplhh_1    
**R script**:  
```{r, echo=TRUE}
table(rowSums(HUNT2[,c("CohAdN_NT2BLQ2","CohChiN_NT2BLQ2")], na.rm=FALSE))

```  

### **Variable label**: Number of children  
**Variable name**: sdc_num_child_1 
**R script**:  
```{r, echo=TRUE}
identical(sdc_HUNT_1$sdc_num_child_1,HUNT2$DelivN_NT2BLQ2)
```

### **Variable label**: Children (biological or adopted)  
**Variable name**: sdc_child_1   
**R script**:  
```{r, echo=TRUE}

```

